---
title: ''
output:
  word_document:
    reference_docx: //conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
# LOCALITY <-  "Skye, Lochalsh and West Ross"
# LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Ayr North and Former Coalfield Communities"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
LOCALITY <-  "Inverness"
#LOCALITY <- "East Dunbartonshire West"

source("~/localities/Master RMarkdown Document & Render Code/Global Script.R")

source("~/localities/Unscheduled Care/2. Unscheduled Care outputs.R")

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```


## Hospital and Community Care

###Summary

This section includes acute hospital data, delayed discharge bed days and A&E attendances.

**For the most recent time periods available, `r LOCALITY` had:**

 - **`r latest_emergency_adm_loc`** emergency hospital admissions per 100,000 population, compared to `r scot_emergency_adm` in Scotland. 
 
 - **`r latest_bed_days_loc`** unscheduled acute specialty bed days per 100,000 population, compared to `r scot_bed_days` in Scotland.  
 
 - **`r latest_ae_att_loc`** A&E attendances per 100,000 population, compared to `r scot_ae_att` in Scotland. 
 
 - **`r latest_dd_loc`** delayed discharge bed days per 100,000 population aged over 65, compared to `r scot_dd` in Scotland. 
 
 - **`r latest_falls_loc`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r scot_falls` in Scotland. 
 
 - **`r latest_read_loc`** emergency readmissions (28 day) per 1,000 discharges, compared to `r scot_read` in Scotland. 
 
 - **`r latest_ppa_loc`** potentially preventable hospital admissions per 100,000 population, compared to `r scot_ppa` in Scotland. 


#####Pagebreak

### Emergency Admissions

####Figure `r x`: Emergency admissions by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
EAs_loc_ts

x <- x + 1
```

####Figure `r x`: Emergency admissions by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
EAs_age_ts

x <- x + 1
```

##### Page break

### Unscheduled Acute Bed Days

####Figure `r x`: Unscheduled acute bed days by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDs_loc_ts

x <- x + 1
```

####Figure `r x`: Unscheduled acute bed days by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDs_age_ts

x <- x + 1
```


##### Page break

### A&E Attendances

####Figure `r x`: A&E attendances by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
AandE_loc_ts

x <- x + 1
```

####Figure `r x`: A&E attendances by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
AandE_age_ts

x <- x + 1
```


##### Page break

### Emergency Readmissions (28 days)

####Figure `r x`: Emergency readmissions (28 days) by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
Read_loc_ts

x <- x + 1
```

####Figure `r x`: Emergency readmissions (28 days) by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
Read_age_ts

x <- x + 1
```


##### Page break

### Delayed Discharge Bed Days

####Figure `r x`: Delayed discharge bed days in population aged 65+ by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
DD_loc_ts

x <- x + 1
```

### Emergency admissions from a fall

####Figure `r x`: Falls in population aged 65+ by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
Falls_loc_ts

x <- x + 1
```


##### Page break

### Potentially Preventable Admissions (PPAs)

Information conditions included in PPAs is available in Appendix 3. In `r max_fy`, **`r latest_ppa_65plus`%** of PPAs in `r LOCALITY` were amongst those aged 65 and over, and **`r latest_ppa_under65`%** were amongst those aged under 65. 

####Figure `r x`: PPAs by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
PPA_loc_ts

x <- x + 1
```
\newline



##### Page break

## Hospital Care (Mental Health Speciality)

###Summary
This section looks at mental health related unscheduled care indicators.

**For the most recent time periods available, `r LOCALITY` had:**

 - **`r psych_hosp_latest`** psychiatric patient hospitalisations per 100,000, compared to `r scot_psych_hosp` in Scotland^4^.
 - **`r latest_bed_days_mh_loc`** unscheduled mental health specialty bed days per 100,000, compared to `r scot_bed_days_mh` in Scotland. 

\newline

### Psychiatric patient hospitalisations

####Figure `r x`: Psychiatric patient hospitalisations by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
psych_hosp_time_trend

x <- x + 1
```


##### Page break

### Unscheduled Mental Health Specialty Bed Days

####Figure `r x`: Unscheduled mental health specialty bed days by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDMH_loc_ts

x <- x + 1
```

####Figure `r x`: Unscheduled mental health specialty bed days by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDMH_age_ts

x <- x + 1
```
