---
title: ''
output:
  word_document:
    reference_docx: //conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
# LOCALITY <-  "Skye, Lochalsh and West Ross"
# LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Ayr North and Former Coalfield Communities"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
LOCALITY <-  "Inverness"
#LOCALITY <- "East Dunbartonshire West"

source("~/list-localities-profiles/Master RMarkdown Document & Render Code/Global Script.R")

source("~/list-localities-profiles/Unscheduled Care/2. Unscheduled Care outputs.R")

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```


## Hospital and Community Care

###Summary

This section includes acute hospital data, delayed discharge bed days and A&E attendances.

**For the most recent time periods available, `r LOCALITY` had:**

 - **`r latest_emergency_adm_loc1`** emergency hospital admissions per 100,000 population, compared to `r scot_emergency_adm1` in Scotland. 
 
 - **`r latest_bed_days_loc1`** unscheduled acute specialty bed days per 100,000 population, compared to `r scot_bed_days1` in Scotland.  
 
 - **`r latest_ae_att_loc`** A&E attendances per 100,000 population, compared to `r scot_ae_att` in Scotland. 
 
 - **`r latest_dd_loc`** delayed discharge bed days per 100,000 population aged over 65, compared to `r scot_dd` in Scotland. 
 
 - **`r latest_falls_loc`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r scot_falls` in Scotland. 
 
 - **`r latest_read_loc`** emergency readmissions (28 day) per 1,000 discharges, compared to `r scot_read` in Scotland. 
 
 - **`r latest_ppa_loc`** potentially preventable hospital admissions per 100,000 population, compared to `r scot_ppa` in Scotland. 


#####Pagebreak

### Emergency Admissions

Figure `r x` presents the emergency admissions rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ea` to `r max_year_ea`. As presented Figure `r x`, the emergency admissions rate in the `r LOCALITY` locality for `r max_year_ea` is `r latest_emergency_adm_loc1`, a `r percent_rate_change`% `r word_change_rate` since `r min_year_ea`. The `r HSCP` HSCP rate is `r hscp_emergency_adm1` in `r max_year_ea`, a `r hscp_rate_change`% `r word_change_hscp` since `r min_year_ea` and the Scotland rate is `r scot_emergency_adm1`, a `r scot_rate_change`% `r word_change_scot` since `r min_year_ea`.

####Figure `r x`: Emergency admissions by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
EAs_loc_ts

x <- x + 1
```

####Figure `r x`: Emergency admissions by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
EAs_age_ts

x <- x + 1
```

##### Page break

### Unscheduled Acute Bed Days

Figure `r x` presents the emergency admissions rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ubd` to `r max_year_ubd`. As presented in Figure `r x`, the emergency admissions rate in the `r LOCALITY` locality for `r max_year_ubd` is `r latest_bed_days_loc1`, a `r rate_change_ubd`% `r word_change_ubd` since `r min_year_ubd`. The `r HSCP` HSCP rate is `r hscp_bed_days1` in `r max_year_ubd`, a `r hscp_rate_ubd`% `r hscp_change_ubd` since `r min_year_ubd` and the Scotland rate is `r scot_bed_days1`, a `r scot_rate_ubd`% `r scot_change_ubd` since `r min_year_ubd`.

####Figure `r x`: Unscheduled acute bed days by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDs_loc_ts

x <- x + 1
```

####Figure `r x`: Unscheduled acute bed days by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDs_age_ts

x <- x + 1
```


##### Page break

### A&E Attendances

Figure `r x` presents the A&E attendance rates per 100,000 population in the `r LOCALITY` locality from `r min_year_ae_area` to `r max_year_ae_area` by geographical area. As presented in Figure `r x`, the A&E attendance rates per 100,000 in `r LOCALITY` for `r max_year_ae_area` is `r latest_ae_att_loc1`, a `r percent_rate_change_ae_areas`% `r word_change_rate_ae_areas` since `r min_year_ae_area`. The `r HSCP` HSCP rate is `r hscp_ae_att1` in `r max_year_ae_area`, a `r percent_rate_change_ae_areas_hscp`% `r word_change_rate_ae_areas_hscp` since `r min_year_ae_area` and the Scotland rate is `r scot_ae_att1`, a `r percent_rate_change_ae_areas_scot`% `r word_change_rate_ae_areas_scot` since `r min_year_ae_area`.

####Figure `r x`: A&E attendances by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
AandE_loc_ts

x <- x + 1
```

####Figure `r x`: A&E attendances by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
AandE_age_ts

x <- x + 1
```


##### Page break

### Emergency Readmissions (28 days)

####Figure `r x`: Emergency readmissions (28 days) by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
Read_loc_ts

x <- x + 1
```

####Figure `r x`: Emergency readmissions (28 days) by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
Read_age_ts

x <- x + 1
```


##### Page break

### Delayed Discharge Bed Days

####Figure `r x`: Delayed discharge bed days in population aged 65+ by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
DD_loc_ts

x <- x + 1
```

### Emergency admissions from a fall

####Figure `r x`: Falls in population aged 65+ by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
Falls_loc_ts

x <- x + 1
```


##### Page break

### Potentially Preventable Admissions (PPAs)

Information conditions included in PPAs is available in Appendix 3. In `r max_fy`, **`r latest_ppa_65plus`%** of PPAs in `r LOCALITY` were amongst those aged 65 and over, and **`r latest_ppa_under65`%** were amongst those aged under 65. 

####Figure `r x`: PPAs by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
PPA_loc_ts

x <- x + 1
```
\newline



##### Page break

## Hospital Care (Mental Health Speciality)

###Summary
This section looks at mental health related unscheduled care indicators.

**For the most recent time periods available, `r LOCALITY` had:**

 - **`r psych_hosp_latest`** psychiatric patient hospitalisations per 100,000, compared to `r scot_psych_hosp` in Scotland^4^.
 - **`r latest_bed_days_mh_loc`** unscheduled mental health specialty bed days per 100,000, compared to `r scot_bed_days_mh` in Scotland. 

\newline

### Psychiatric patient hospitalisations

####Figure `r x`: Psychiatric patient hospitalisations by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
psych_hosp_time_trend

x <- x + 1
```


##### Page break

### Unscheduled Mental Health Specialty Bed Days

####Figure `r x`: Unscheduled mental health specialty bed days by geographical area
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDMH_loc_ts

x <- x + 1
```

####Figure `r x`: Unscheduled mental health specialty bed days by age group
\newline

```{r echo = FALSE, fig.width= 7.6, fig.height= 4, warning = F}
BDMH_age_ts

x <- x + 1
```
