---
title: ''
output:
  word_document:
    reference_docx: //conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx
  html_document:
    df_print: paged
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
# LOCALITY <- "Skye, Lochalsh and West Ross"
# LOCALITY <- "Ayr North and Former Coalfield Communities"


source("~/localities/Master RMarkdown Document & Render Code/Global Script.R")

# For testing - CF directory
source("~/localities/Lifestyle & Risk Factors/2. Lifestyle & Risk Factors Outputs.R")

# KH testing directory

# source("~/list-localities-profiles/Lifestyle & Risk Factors/2. Lifestyle & Risk Factors Outputs.R")



x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```

##### Page break

## Lifestyle and Risk Factors

\newline

### Summary

Mental and physical wellbeing has close ties with people's lifestyles and behaviours. Financial security, employment and location are influences that often have a bearing on these choices. Issues can develop when alcohol, smoking or drug use shape lives. This section provides data on drug-related hospital admissions, alcohol-related hospital admissions, alcohol-specific deaths and bowel screening uptake, to give an overview of some of the lifestyles and behaviours for `r LOCALITY` locality. These can give an idea of quality of life and prosperity.


\newline

**For the most recent time periods available^3^, `r LOCALITY` had:**

- **`r format_number_for_text(alcohol_hosp_latest)`** alcohol-related hospital admissions per 100,000 age-sex standardised population. This is `r alcohol_hosp_diff_scot` than Scotland (`r  format_number_for_text(scot_alcohol_hosp)` admissions per 100,000)^4^.
- **`r format_number_for_text(alcohol_deaths_latest)`** alcohol-specific deaths per 100,000 age-sex standardised population. This is `r alcohol_deaths_diff_scot` than Scotland (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000)^4^.
- **`r format_number_for_text(drug_hosp_latest)`** drug-related hospital admissions per 100,000 age-sex standardised population. This is `r drug_hosp_diff_scot` than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000)^4^.
- **`r format_number_for_text(bowel_screening_latest)`%** uptake of bowel screening among eligible population, compared to `r format_number_for_text(scot_bowel_screening)`% in Scotland.

\newline


###Alcohol-related Hospital Admissions

In `r latest_period_alcohol_hosp`, the rate of alcohol-related admissions was **`r format_number_for_text(alcohol_hosp_latest)`** per 100,000 age-sex standardised population in `r LOCALITY`. This is a `r format_number_for_text(alcohol_hosp_change)`% `r alcohol_hosp_change_word` overall since `r earliest_period_alcohol_hosp`. Figure `r x` shows a trend of alcohol-related hospital admissions for `r LOCALITY` locality compared with Scotland, `r HSCP` HSCP and `r HB` from financial year `r earliest_period_alcohol_hosp` to `r latest_period_alcohol_hosp`. 

Figure `r x + 1` then compares different areas, including the other localities in `r HSCP`, for the latest financial year. This bar chart shows that in `r latest_period_alcohol_hosp`, `r LOCALITY` locality had a `r alcohol_hosp_diff_scot` alcohol-related hospital admissions rate compared to Scotland (`r format_number_for_text(alcohol_hosp_latest)` and `r  format_number_for_text(scot_alcohol_hosp)` admissions respectively).


#####Page break

#### Figure `r x`: Alcohol-related hospital admission rates by area and over time.
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4, warning = FALSE}
alcohol_hosp_time_trend

x <- x + 1
```

#### Figure `r x`: Alcohol-related hospital admissions by area for the latest time period.
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE}
alcohol_hosp_bar

x <- x + 1
```

\newline

###Alcohol-Specific Deaths

Data on alcohol-specific deaths is available as 5-year aggregates. In `r LOCALITY`, the latest rate of alcohol-specific deaths was **`r format_number_for_text(alcohol_deaths_latest)`** deaths per 100,000 age-sex standardised population. This is `r format_number_for_text(alcohol_deaths_change)`% `r alcohol_deaths_change_word` than the rate in `r earliest_period_alcohol_deaths`. Figure `r x + 1` also shows that the locality has a `r alcohol_deaths_diff_scot` alcohol-specific death rate compared to Scotland overall (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000).

#### Figure `r x`: Alcohol-specific deaths by area and over time.
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 3.6, warning = FALSE}
alcohol_deaths_time_trend

x <- x + 1
```

#### Figure `r x`: Alcohol-specific deaths by area for the latest time period available.
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.5, warning = FALSE}
alcohol_deaths_bar

x <- x + 1
```

\newline

###Drug-related Hospital Admissions

There were **`r format_number_for_text(drug_hosp_latest)`** drug-related hospital admissions per 100,000 age-sex standardised population^4^ in `r LOCALITY` locality in the time period `r latest_period_drug_hosp` (3-year financial year aggregate). This is a `r format_number_for_text(drug_hosp_change)`% `r drug_hosp_change_word` since `r earliest_period_drug_hosp`. A trend of the change in drug-related hospital admissions for the locality and comparable areas is shown in figure `r x` from `r earliest_period_drug_hosp` onward.

A comparison of areas at the most recent time period  (`r latest_period_drug_hosp` aggregated financial years) is available in figure `r x + 1` This shows `r LOCALITY` locality has a `r drug_hosp_diff_scot` rate of drug-related hospital admissions than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000).

#### Figure `r x`: Drug-related hospital admission rates by area and over time.
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4, warning = FALSE}
drug_hosp_time_trend

x <- x + 1
```

#####Page break

#### Figure `r x`: Drug-related hospital admission rates by area for the latest time period available.

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE}
drug_hosp_bar

x <- x + 1
```

\newline

###Bowel Screening Uptake

Bowel screening is offered every two years to eligible men and women aged between 50-74 years old. Eligible people are posted a test kit which is completed at home. Since 1st April 2013, those aged 75 and over can also self-refer and opt into screening.

A trend of the percentage uptake of bowel screening among the eligible population is shown the locality and comparable areas. Data is suppressed into 3-year aggregates. The `r latest_period_bowel_screening` uptake rate for `r LOCALITY` is **`r format_number_for_text(bowel_screening_latest)`%**. This is a `r format_number_for_text(bowel_screening_change)`% `r bowel_screening_change_word` since `r earliest_period_bowel_screening`. As can be seen in figure `r x + 1`, in the latest estimate, the uptake in `r LOCALITY` was `r bowel_screening_diff_scot` than the uptake in Scotland overall (`r format_number_for_text(scot_bowel_screening)`%).


##### Page break

#### Figure `r x`: Bowel screening uptake for eligible men and women, by area and over time. 
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4, warning = FALSE}
bowel_screening_time_trend

x <- x + 1
```

#### Figure `r x`: Bowel screening uptake by area for the latest time period available.
\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE}
bowel_screening_bar

x <- x + 1
```

