---
output: 
  phstemplates::phs_report_docx:
    reference_docx: "/conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality Profiles/Master RMarkdown Document & Render Code/phs-mngtinfo-report.docx"
    fig_caption: no
    cover_page: "/conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality Profiles/Master RMarkdown Document & Render Code/phs-mngtinfo-cover.docx"
    cover_title: "My Title"
    cover_subtitle: "My subtitle"
    cover_date: "DD MM YYYY"
    toc_depth: 3
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
# LOCALITY <- "Skye, Lochalsh and West Ross"
# LOCALITY <- "Ayr North and Former Coalfield Communities"

source("Households/Households Code.R")

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```

# Housing

**Summary**

For the most recent time period available, `r LOCALITY` Locality had:

* **`r n_houses`** dwellings, of which: **`r perc_occupied`%** were occupied and **`r perc_second_homes`%** were second homes.
* **`r perc_single_discount`%** of dwellers received a single-occupant council tax discount, and **`r perc_exempt`%** were exempt from council tax entirely.
* **`r perc_houses_AC`%** of houses were within council tax bands A to C, and **`r perc_houses_FH`%** were in bands F to H.

The graph below shows the number of dwellings in `r LOCALITY` from `r min(house_dat$year)` to `r max_year_housing`.

<Div custom-style = "Table or chart caption">Figure `r x`: Number of dwellings time trend.</Div>

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE}
houses_ts

x <- x + 1
```

Of the total number of dwellings in `r max_year_housing`, `r perc_single_discount`% (`r n_single_discount` households) were occupied by an individual receiving a single-occupant council tax discount. Furthermore, `r perc_exempt`% (`r n_exempt` households) were occupied and exempt from council tax.

There were `r n_second_homes` dwellings classed as a second home in `r max_year_housing`, these dwellings made up `r perc_second_homes`% of the households in `r LOCALITY`.

<Div custom-style = "Table or chart caption">Table `r y`: Breakdown of dwelling types by year for `r LOCALITY` locality.</Div>
```{r echo = FALSE}
flextable(house_table, theme_fun = NULL) %>%
  my_ft_format() %>%
  set_header_labels(values = c(
    "Year", "Total Dwellings", "Occupied Dwellings",
    "Vacant Dwellings", "Single Occupant Tax Discount", 
    "Council Tax Exempt Dwellings", "Second Homes"
  )) %>%
  bold(i = nrow(house_table)) %>%
  width(width = 6.5/ncol(house_table))


y <- y + 1
```

Source: Scottish Assessors' Association (via NRS) \newline

The proportion of households within each council tax band are displayed in the chart below, figures are shown in Table `r y`.

<Div custom-style = "Table or chart caption">Figure `r x`: Breakdown of households by council tax band for `r LOCALITY` in `r max_year_housing`.</Div>

```{r echo = FALSE, fig.width = 7, fig.height = 2, warning = FALSE, fig.cap = 'A bar graph showing the proportion of Households in each council tax band for the locality for the most recent year'}
ctb_plot

x <- x + 1
```

<Div custom-style = "Table or chart caption">Table `r y`: Percentage of households by council tax band for `r LOCALITY` in `r max_year_housing`.</Div>

```{r echo = FALSE}

flextable(ctb_table, theme_fun = NULL) %>%
  my_ft_format() %>%
  set_header_labels(values = c(
     "Tax Band", "A", "B", "C",
    "D", "E", "F", "G", "H"
  )) %>% 
  width(j = 1, width = 1.12) %>%           
  width(j = 2:9, width = 0.77)

```
Source: Scottish Assessors' Association (via NRS)
