---
title: ''
output:
  word_document:
    reference_docx: "/conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx"
  html_document:
    df_print: paged
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

# Line below for testing only
# LOCALITY <- "Falkirk West"
# LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
# LOCALITY <- "Helensburgh and Lomond"
# LOCALITY <- "City of Dunfermline"
# LOCALITY <- "Skye, Lochalsh and West Ross"
# LOCALITY <- "Ayr North and Former Coalfield Communities"

source("Households/Households Code.R")

x <- 1 # object for figure numbers
y <- 1 # object for table numbers
```

## Housing

\newline

**Summary**

For the most recent time period available, `r HSCP` HSCP had:

-   **`r n_houses`** dwellings, of which: **`r perc_occupied`%** were occupied and **`r perc_second_homes`%** were second homes.
-   **`r perc_single_discount`%** of dwellers received a single-occupant council tax discount, and **`r perc_exempt`%** were exempt from council tax entirely.
-   **`r perc_houses_AC`%** of houses were within council tax bands A to C, and **`r perc_houses_FH`%** were in bands F to H.

\newline

The graph below shows the number of dwellings in `r HSCP` from `r min(house_dat$year)` to `r max_year_housing`.

#### Figure `r x`: Number of dwellings time trend.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE}
houses_ts

x <- x + 1
```

Of the total number of dwellings in `r max_year_housing`, `r perc_single_discount`% (`r n_single_discount` households) were occupied by an individual receiving a single-occupant council tax discount. Furthermore, `r perc_exempt`% (`r n_exempt` households) were occupied and exempt from council tax.

There were `r n_second_homes` dwellings classed as a second home in `r max_year_housing`, these dwellings made up `r perc_second_homes`% of the households in `r HSCP`.

##### Page break

#### Table `r y`: Breakdown of dwelling types by year for `r HSCP` HSCP.

\newline

```{r echo = FALSE}
knitr::kable(house_table,
  col.names = c(
    "**Year**", "**Total Dwellings**", "**Occupied Dwellings**",
    "**Vacant Dwellings**", "**Single Occupant Tax Discount**", "**Council Tax Exempt Dwellings**", "**Second Homes**"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r"), format = "markdown"
)

y <- y + 1
```

Source: Scottish Assessors' Association (via NRS) \newline

The proportion of households within each council tax band are displayed in the chart below, figures are shown in Table `r y`.

#### Figure `r x`: Breakdown of households by council tax band for `r HSCP` in `r max_year_housing`.

\newline

```{r echo = FALSE, fig.width = 7, fig.height = 2, warning = FALSE, fig.cap = 'A bar graph showing the proportion of Households in each council tax band for the locality for the most recent year'}
ctb_plot

x <- x + 1
```

#### Table `r y`: Percentage of households by council tax band for `r HSCP` in `r max_year_housing`.

\newline

```{r echo = FALSE}
knitr::kable(ctb_table,
  col.names = c(
    "**Tax Band**", "**A**", "**B**", "**C**",
    "**D**", "**E**", "**F**", "**G**", "**H**"
  ),
  align = c("l", rep("r", 8)), format = "markdown"
)

y <- y + 1
```

Source: Scottish Assessors' Association (via NRS)
