---
title: "Localities Profiles"
author: "Public Health Scotland"
site: bookdown::bookdown_site
documentclass: book
---

```{r,echo=FALSE}
library(officedown)

table_heading_style <- fp_text(
  color = "#43358B",
  font.size = 12,
  bold = TRUE,
  font.family = "Arial"
)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(kableExtra.auto_format = FALSE)

figure_num <- 1 # object for figure numbers
table_num <- 1 # object for table numbers
```

<!--chapter:end:index.Rmd-->


```{r load_packages, include=FALSE}
library(knitr)
library(flextable)
library(officer)
library(officedown)
```

\newpage

<!---BLOCK_LANDSCAPE_START--->

```{r, include=FALSE}
block_section(prop_section(type = "continuous"))
```

# Summary Table

```{r locality_names, include=FALSE}
# Set locality name object (with automatic wrapping)
loc_name <- paste(LOCALITY, "Locality", sep = "\n") |>
  str_wrap(width = case_when(n_loc < 4 ~ 20, n_loc == 4 ~ 15, n_loc > 4 ~ 8))

# Set other localities names
other_loc_names <- paste(other_locs$hscp_locality, "Locality", sep = "\n") |>
  str_wrap(width = case_when(n_loc < 4 ~ 20, n_loc == 4 ~ 15, n_loc > 4 ~ 8))

# Set HSCP name object
hscp_name <- paste(HSCP, "HSCP") |>
  str_wrap(width = if_else(n_loc < 3, 25, 10))

# Set the headings (We will add the first heading per table)
headings <- c(
  "Data Type",
  "Time Period",
  loc_name,
  other_loc_names,
  hscp_name,
  "Scotland"
)
```

```{r summary_table_func, include=FALSE}
make_summary_table <- function(data) {
  info_cols <- 1:3
  loc_col <- 4
  other_loc_cols <- 5:(ncol(data) - 2)
  hscp_col <- ncol(data) - 1
  scot_col <- ncol(data)

  data |>
    mutate(
      # Remove odd spaces in numbers
      across(all_of(c(loc_col, other_loc_cols, hscp_col, scot_col)), str_squish),
      # Make any missing values a dash
      across(all_of(c(loc_col, other_loc_cols, hscp_col, scot_col)), \(figure_num) na_if(figure_num, "NA")),
      across(all_of(c(loc_col, other_loc_cols, hscp_col, scot_col)), \(figure_num) replace_na(figure_num, "-"))
    ) |>
    flextable() |>
    # Header
    font(part = "header", fontname = "Arial") |>
    fontsize(part = "header", size = 10) |>
    bold(part = "header") |>
    color(part = "header", color = "white") |>
    bg(part = "header", bg = phs_colours("phs-purple")) |>
    # Indicators column (col 1)
    bold(j = 1, part = "body") |>
    # Main content
    font(part = "body", fontname = "Arial") |>
    fontsize(part = "body", size = 10) |>
    bg(j = info_cols, part = "body", bg = phs_colours("phs-graphite-30")) |>
    bg(j = loc_col, part = "body", bg = phs_colours("phs-purple-30")) |>
    bg(j = other_loc_cols, part = "body", bg = phs_colours("phs-magenta-30")) |>
    bg(j = hscp_col, part = "body", bg = phs_colours("phs-blue-30")) |>
    bg(j = scot_col, part = "body", bg = phs_colours("phs-green-30")) |>
    border(border = fp_border(color = "white", width = 1), part = "body") |>
    set_table_properties(layout = "autofit")
}
```

```{r demographics}
indicators <- c(
  "Total population",
  "Ratio male to female",
  "Population over 65",
  "Population in the least deprived SIMD quintile",
  "Population in the most deprived SIMD quintile"
)
# List what data type they are
datatype <- c("count", "ratio", "%", "%", "%")
# Enter the time periods available
time <- c(pop_max_year, pop_max_year, pop_max_year, "2020", "2020")

loc_values <- c(total_population, paste0("1:", gender_ratio), over65, perc_top_quintile, perc_bottom_quintile)

other_loc_values <- rbind(other_locs_total_pop, other_locs_gender_ratio, other_locs_over65, other_locs_simd)
hscp_values <- c(hscp_total_pop, hscp_gender_ratio, hscp_over65, hscp_simd_top, hscp_simd_bottom)
scot_values <- c(scot_total_pop, scot_gender_ratio, scot_over65, 20, 20)

demographic_values <- tibble(
  indicators, datatype, time, loc_values, other_loc_values,
  hscp_values, scot_values
)

colnames(demographic_values) <- c("Demographic Indicators", headings)

demographics_table <- make_summary_table(demographic_values)

demographics_table
```
\newline
######

```{r housing}
indicators <- c(
  "Total number of households",
  "Households with single occupant tax discount",
  "Households in Council Tax Band A-C",
  "Households in Council Tax Band F-H"
)

datatype <- c("count", "%", "%", "%")

time <- as.character(c(max_year_housing, max_year_housing, max_year_housing, max_year_housing))

# Values
loc_values <- c(n_houses, perc_single_discount, perc_houses_AC, perc_houses_FH)
other_loc_values <- rbind(other_locs_n_houses, other_locs_perc_discount, other_locs_perc_housesAC, other_locs_perc_housesFH)
hscp_values <- c(hscp_n_houses, hscp_perc_discount, hscp_perc_housesAC, hscp_perc_housesFH)
scot_values <- c(scot_n_houses, scot_perc_discount, scot_perc_housesAC, scot_perc_housesFH)


housing_values <- tibble(
  indicators, datatype, time, loc_values, other_loc_values,
  hscp_values, scot_values
)

colnames(housing_values) <- c("Housing Indicators", headings)

housing_table <- make_summary_table(housing_values)

housing_table
```
\newline
######

```{r general_health}
indicators <- c(
  "Male average life expectancy in years",
  "Female average life expectancy in years",
  "Deaths aged 15-44 per 100,000",
  "Population estimated to have at least one LTC",
  "Cancer registrations per 100,000",
  "Anxiety, depression & psychosis prescriptions"
)

datatype <- c("mean", "mean", "rate", "%", "rate", "%")

time <- c(
  paste0(latest_period_life_exp_loc, "*"),
  paste0(latest_period_life_exp_loc, "*"),
  latest_period_deaths_15_44,
  latest_year_ltc,
  latest_period_cancer_reg,
  latest_period_adp_presc
)

# Values

loc_values <- round_half_up(c(avg_life_exp_latest_male, avg_life_exp_latest_fem, deaths_15_44_latest, ltc_percent_total_latest, cancer_reg_rate_latest, adp_presc_latest), 1)
other_loc_values <- rbind(other_locs_life_exp_male, other_locs_life_exp_fem, other_locs_deaths_15_44, other_locs_ltc, other_locs_cancer, other_locs_adp)
hscp_values <- c(hscp_life_exp_male, hscp_life_exp_fem, hscp_deaths_15_44, hscp_ltc, hscp_cancer, hscp_adp)
scot_values <- c(scot_life_exp_male, scot_life_exp_fem, scot_deaths_15_44, ltc_perc_scot, scot_cancer, scot_adp_presc)

general_health_values <- tibble(
  indicators, datatype, time, loc_values, other_loc_values,
  hscp_values, scot_values
)

colnames(general_health_values) <- c("General Health Indicators", headings)

general_health_table <- make_summary_table(general_health_values)

general_health_table
```

###### \*At HSCP and Scotland level, the time period is a 3-year aggregate (`r latest_period_life_exp_otherareas`)
\newline
```{r lifestyle_risk_factors}
indicators <- c(
  "Alcohol-related hospital admissions per 100,000",
  "Alcohol-specific mortality per 100,000",
  "Drug-related hospital admissions per 100,000",
  "Bowel screening uptake"
)

datatype <- c("rate", "rate", "rate", "%")

time <- c(
  latest_period_alcohol_hosp,
  latest_period_alcohol_deaths,
  str_wrap(latest_period_drug_hosp, 9),
  latest_period_bowel_screening
)

# Values
loc_values <- round_half_up(c(alcohol_hosp_latest, alcohol_deaths_latest, drug_hosp_latest, bowel_screening_latest), 1)
other_loc_values <- rbind(other_locs_alcohol_hosp, other_locs_alcohol_deaths, other_locs_drug_hosp, other_locs_bowel_screening)
hscp_values <- c(hscp_alcohol_hosp, hscp_alcohol_deaths, hscp_drug_hosp, hscp_bowel_screening)
scot_values <- c(scot_alcohol_hosp, scot_alcohol_deaths, scot_drug_hosp, scot_bowel_screening)


lifestyle_values <- tibble(
  indicators, datatype, time, loc_values, other_loc_values,
  hscp_values, scot_values
)

colnames(lifestyle_values) <- c("Lifestyle & Risk Factors Indicators", headings)

lifestyle_table <- make_summary_table(lifestyle_values)

lifestyle_table
```
\newline
######

```{r hospital_community_care}
indicators <- c(
  "Emergency admissions per 100,000",
  "Unscheduled bed days per 100,000",
  "A&E attendances per 100,000",
  "Delayed discharges (65+) per 100,000",
  "Potentially Preventable Admissions per 100,000"
)
datatype <- c("rate", "rate", "rate", "rate", "rate")
time <- c(max_fy, max_fy, max_fy, max_fy, max_fy)

# Values
loc_values <- format(
  c(latest_emergency_adm_loc1, latest_bed_days_loc1, latest_ae_att_loc1, latest_dd_loc1, latest_ppa_loc1),
  big.mark = ","
)
other_loc_values <- bind_rows(other_loc_emergency_adm, other_loc_bed_days, other_loc_ae_att, other_loc_dd, other_loc_ppa)
hscp_values <- format(
  c(hscp_emergency_adm$data, hscp_bed_days$data, hscp_ae_att$data, hscp_dd$data, filter(hscp_ppa, year == max(year))$data),
  big.mark = ","
)
scot_values <- format(
  c(scot_emergency_adm$data, scot_bed_days$data, scot_ae_att$data, scot_dd$data, filter(scot_ppa, year == max(year))$data),
  big.mark = ","
)

usc_values <- tibble(
  indicators, datatype, time, loc_values, other_loc_values,
  hscp_values, scot_values
)

colnames(usc_values) <- c("Hospital & Community Care Indicators", headings)

usc_table <- make_summary_table(usc_values)

usc_table
```
\newline
######

```{r hospital_mental_health}
indicators <- c(
  "Psychiatric patient hospitalisations per 100,000",
  "Unscheduled bed days per 100,000"
)
datatype <- c("rate", "rate")
time <- c(str_wrap(latest_period_psych_hosp, 9), max_fy)

# Values
loc_values <- c(
  format(psych_hosp_latest, big.mark = ","),
  format(
    ifelse(is_empty(latest_bed_days_mh_loc1), NA_real_, latest_bed_days_mh_loc1),
    big.mark = ","
  )
)

other_loc_values <- bind_rows(other_locs_psych_hosp, other_loc_bed_days_mh)
hscp_values <- c(
  format(filter(hscp_psych_hosp, year == max(year))$measure, big.mark = ","),
  format(hscp_bed_days_mh$data, big.mark = ",")
)
scot_values <- c(
  format(filter(scot_psych_hosp, year == max(year))$measure, big.mark = ","),
  format(scot_bed_days_mh$data, big.mark = ",")
)


usc_mh_values <- tibble(
  indicators, datatype, time, loc_values, other_loc_values,
  hscp_values, scot_values
)

colnames(usc_mh_values) <- c("Hospital Care (Mental Health) Indicators", headings)

usc_mh_table <- make_summary_table(usc_mh_values)

usc_mh_table
```

\newpage

```{r, include=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape")))
```

<!--chapter:end:Summary-Table.Rmd-->


# Notes for this profile

\newline

-   All years shown are calendar years unless otherwise specified.

-   Upper and lower 95% confidence intervals are shown throughout this document where available. In charts, these are displayed as shaded areas on either side of trend lines or as black error bars in bar charts. Confidence intervals show the range of possible values and a certainty that the true value falls within them.

-   Definitions for the indicators shown are available in Appendix 1.

-   Any zero figures for some indicators will indicate either suppression of small data or a complete lack of data available for this locality.

<!--chapter:end:Notes-On-Profile.Rmd-->


\newpage

# Demographics

\newline

**Summary**

For the most recent time period available, `r LOCALITY` Locality had:

-   A total population of **`r total_population`** people, where **`r gender_breakdown[gender_breakdown$sex == "M",]$perc`** were male, and **`r over65`%** were aged over 65.
-   **`r perc_top_quintile`%** of people lived in the least deprived SIMD quintile, and **`r perc_bottom_quintile`%** lived in the most deprived quintile.

\newline

### Population

<!-- Total Population Text -->

In `r pop_max_year`, the total population of `r LOCALITY` locality was `r total_population`. The graph below shows the population distribution of the locality. Overall, **`r gender_breakdown[gender_breakdown$sex == "M",]$perc`** of the population are male, and **`r gender_breakdown[gender_breakdown$sex == "F",]$perc`** are female.

<!-- <Div custom-style = "Table or chart caption"></Div> -->

`r ftext(paste0("Figure ",figure_num,": Population by age and sex."),table_heading_style)`

```{r fig.width = 7, fig.height = 4, warning = FALSE, fig.cap = "A bar chart showing the population distribution of the locality grouped by age and sex"}
pop_pyramid

figure_num <- figure_num + 1
```

<!-- Population over time -->

Figure `r figure_num` shows the historical population of `r LOCALITY`, along with the NRS population projections. `r pop_graph_text` `r pop_proj_text`. *Please see the footnotes for more information on how the population projections were calculated^1^.*

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Population time trend and projection.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Population time trend and projection."),table_heading_style)`

```{r fig.width = 7.5, fig.height = 4, warning = FALSE, fig.cap= "A line graph showing the trend in population over time"}
pop_ts_plot

figure_num <- figure_num + 1
```

\newline

Figure `r figure_num` shows how the population structure has changed between `r pop_min_year` and `r pop_max_year`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Change in population structure over the last five years.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Change in population structure over the last five years."),table_heading_style)`

```{r fig.width = 9, fig.height = 4, warning = FALSE, fig.cap= "A bar chart showing the percentage change in population structure, split by age and sex, over the last five years"}
hist_pop_change

figure_num <- figure_num + 1
```

### Deprivation

The following section explores the deprivation structure of `r LOCALITY` through the Scottish Index of Multiple Deprivation (SIMD). The SIMD ranks all datazones in Scotland by a number of factors; Access, Crime, Education, Employment, Health, Housing and Income. Based on these ranks, each datazone is then given an overall deprivation rank, which is used to split datazones into Deprivation Quintiles (Quintile 1 being the most deprived, and Quintile 5 the least). The most recent SIMD ranking was carried out in 2020. This section mainly focuses on the SIMD 2020 classifications, however, the 2016 classifications are used to assess how deprivation has changed in `r LOCALITY` when compared to the rest of Scotland.

Of the `r pop_max_year` population in `r LOCALITY`, **`r perc_bottom_quintile`%** live in the most deprived Quintile (SIMD 1), and **`r perc_top_quintile`%** live in the least deprived Quintile (SIMD 5).

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Map of Data Zones within `r LOCALITY` coloured by SIMD quintiles.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Map of Data Zones within ",LOCALITY," coloured by SIMD quintiles."),table_heading_style)`


```{r fig.width = 8, warning = FALSE, fig.cap = 'A map of the locality which is broken down by data zones with the colouring showing the SIMD quintile for each.'}
simd_map

figure_num <- figure_num + 1
```

##### Page break

Table `r table_num` details the percentage of the locality's 2016 population living in the 2016 SIMD Quintiles, the percentage of the `r pop_max_year` population living in the 2020 SIMD Quintiles, and their difference for comparison. Figure `r figure_num` then breaks down SIMD by domain in `r LOCALITY`.

<!-- <Div custom-style = "Table or chart caption">Table `r table_num`: Percentage of the `r LOCALITY` population living in the 2016 and 2020 SIMD Datazone Quintiles in 2016 and `r pop_max_year` respectively.</Div> -->

`r ftext(paste0("Table ",table_num,": Percentage of the ", LOCALITY," population living in the 2016 and 2020 SIMD Datazone Quintiles in 2016 and ", pop_max_year," respectively."),table_heading_style)`



```{r }
flextable(simd_diff_overall, theme_fun = NULL) |>
  lp_flextable_theme() |>
  set_header_labels(values = c(
    "Quintile", "Percent of 2016 Population (SIMD 2016 Ranking)",
    glue("Percent of {pop_max_year} Population (SIMD 2020 Ranking)"),
    "Difference"
  )) |>
  width(j = 1, width = 1) |>
  width(j = 4, width = 1) |>
  width(j = 2:3, width = 2.2)

table_num <- table_num + 1
```

Source: Scottish Government, Public Health Scotland, National Records Scotland. \newline

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Proportion of the population that reside in each 2020 SIMD quintile by domain in `r pop_max_year`.</Div> -->


`r ftext(paste0("Figure ",figure_num,": Proportion of the population that reside in each 2020 SIMD quintile by domain in ",pop_max_year,"."),table_heading_style)`

```{r fig.width = 8, fig.height = 5, warning = FALSE, fig.cap = 'A bar graph showing the proportion of the population in each SIMD decile for each SIMD domain.'}
simd_domains

figure_num <- figure_num + 1
```


Figure `r figure_num` presents a comparison between the 2016 SIMD ranking applied to 2016 population estimates, and the more recent 2020 SIMD ranking applied to `r pop_max_year` population estimates. The percentages of the population living within each SIMD quintile by domain were calculated using the 2016 and 2020 SIMD datazone classifications respectively. The differences in these percentages are plotted in Figure `r figure_num`. Negative values on the y-axis indicate a decrease in the percent of the population living within a quintile, while positive values indicate an increase in the percent of the population living within a quintile. **Please note that quintiles have been weighted by the Scottish population so, any local changes in SIMD quintile do not necessarily indicate a difference in deprivation, but rather a difference in deprivation in comparison to the rest of Scotland.**

\newline

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Percentage of population in 2016 and `r pop_max_year` living in the 2016 and the 2020 SIMD quintiles by domain.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Percentage of population in 2016 and ",pop_max_year," living in the 2016 and the 2020 SIMD quintiles by domain."),table_heading_style)`


\newline

```{r fig.width = 7.5, fig.height = 7, warning = FALSE, fig.cap = 'Bar graphs showing the percentage change of the population in each SIMD quintile by SIMD domain'}
simd_diff_plot

figure_num <- figure_num + 1
```

<!--chapter:end:Demographics.Rmd-->


\newpage

# Services

\newline
<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Map of services by locality in `r HSCP` HSCP^2^</Div> -->

`r ftext(paste0("Figure ",figure_num,": Map of services by locality in ", HSCP," HSCP^2"),table_heading_style)`


```{r fig.width=6, fig.cap= "A map of the health and social care partnership including a breakdown on localities with the locations of all the GP practices, care homes, emergency depertments and minor injury units."}
service_map

figure_num <- figure_num + 1
```


\newline
<!-- <Div custom-style = "Table or chart caption">Table `r table_num`: Number of each type of service in `r LOCALITY` Locality^2^</Div> -->

`r ftext(paste0("Table ",table_num,": Number of each type of service in ",LOCALITY," Locality^2"),table_heading_style)`


```{r }
flextable(services_tibble, theme_fun = NULL) |>
  lp_flextable_theme() |>
  set_header_labels(values = c("Service Type", "Service", "Number")) |>
  set_table_properties(layout = "autofit")

table_num <- table_num + 1
```

<!--chapter:end:Services.Rmd-->


\newpage

# Housing

\newline

**Summary**

For the most recent time period available, `r LOCALITY` Locality had:

-   **`r n_houses`** dwellings, of which: **`r perc_occupied`%** were occupied and **`r perc_second_homes`%** were second homes.
-   **`r perc_single_discount`%** of dwellers received a single-occupant council tax discount, and **`r perc_exempt`%** were exempt from council tax entirely.
-   **`r perc_houses_AC`%** of houses were within council tax bands A to C, and **`r perc_houses_FH`%** were in bands F to H.

\newline

The graph below shows the number of dwellings in `r LOCALITY` from `r min(house_dat$year)` to `r max_year_housing`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Number of dwellings time trend.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Number of dwellings time trend."),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE}
houses_ts

figure_num <- figure_num + 1
```

Of the total number of dwellings in `r max_year_housing`, `r perc_single_discount`% (`r n_single_discount` households) were occupied by an individual receiving a single-occupant council tax discount. Furthermore, `r perc_exempt`% (`r n_exempt` households) were occupied and exempt from council tax.

There were `r n_second_homes` dwellings classed as a second home in `r max_year_housing`, these dwellings made up `r perc_second_homes`% of the households in `r LOCALITY`.


<!-- <Div custom-style = "Table or chart caption">Table `r table_num`: Breakdown of dwelling types by year for `r LOCALITY` locality.</Div> -->

`r ftext(paste0("Table ",table_num,": Breakdown of dwelling types by year for ",LOCALITY," locality."),table_heading_style)`


```{r }
flextable(house_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  set_header_labels(values = c(
    "Year", "Total Dwellings", "Occupied Dwellings",
    "Vacant Dwellings", "Single Occupant Tax Discount", "Council Tax Exempt Dwellings", "Second Homes"
  )) |>
  set_table_properties(layout = "autofit")

table_num <- table_num + 1
```

Source: Scottish Assessors' Association (via NRS) \newline

The proportion of households within each council tax band are displayed in the chart below, figures are shown in Table `r table_num`.


<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Breakdown of households by council tax band for `r LOCALITY` in `r max_year_housing`.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Breakdown of households by council tax band for ",LOCALITY," in ",max_year_housing,"."),table_heading_style)`

```{r fig.width = 7, fig.height = 2, warning = FALSE, fig.cap = 'A bar graph showing the proportion of Households in each council tax band for the locality for the most recent year'}
ctb_plot

figure_num <- figure_num + 1
```


<!-- <Div custom-style = "Table or chart caption">Table `r table_num`: Percentage of households by council tax band for `r LOCALITY` in `r max_year_housing`.</Div> -->

`r ftext(paste0("Table ",table_num,": Percentage of households by council tax band for ",LOCALITY," in ",max_year_housing,"."),table_heading_style)`


```{r }
flextable(ctb_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  set_header_labels(values = c(
    "Tax Band", "A", "B", "C",
    "D", "E", "F", "G", "H"
  ))

table_num <- table_num + 1
```

Source: Scottish Assessors' Association (via NRS)

<!--chapter:end:Housing.Rmd-->

\newpage

# General Health

### Summary

\newline

For the most recent time period available^3^, `r LOCALITY` Locality had:

```{r life_exp_text}
if (is.na(avg_life_exp_latest_male)) {
  life_exp_text <- "No data available for life expectancy."
  life_exp_text2 <- "No data available for life expectancy at locality level."
} else {
  life_exp_text <- glue("An average life expectancy of **{avg_life_exp_latest_male}** years for males and **{avg_life_exp_latest_fem}** years for females, compared to the national average of {scot_life_exp_male} and {scot_life_exp_fem} years of age respectively.")
  life_exp_text2 <- glue("In the latest time period available from {latest_period_life_exp_loc} (5-year aggregate), the average life expectancy in {LOCALITY} locality was {avg_life_exp_latest_male} years for men, and {avg_life_exp_latest_fem} years for women. A 10-year time trend can be seen in figure {figure_num}.")
}
```

-   `r life_exp_text`
-   A death rate for ages 15 to 44 of **`r format_number_for_text(deaths_15_44_latest)`** deaths per 100,000 age-sex standardised population. This is `r deaths_15_44_diff_scot` than Scotland (`r format_number_for_text(scot_deaths_15_44)` deaths per 100,000)^4^.
-   **`r format_number_for_text(ltc_percent_total_latest)`%** of the locality's population with at least one long-term physical health condition. This is `r ltc_diff_scot` than Scotland (`r format_number_for_text(ltc_perc_scot)`%).
-   A cancer registration rate of **`r format_number_for_text(cancer_reg_rate_latest)`** registrations per 100,000 age-sex standardised population (compared to `r format_number_for_text(scot_cancer)` in Scotland), and an early death rate (\<75 years) from cancer of **`r format_number_for_text(early_deaths_cancer_rate_latest)`** per 100,000 age-sex standardised population (compared to `r format_number_for_text(scot_cancer_deaths)` in Scotland)^4^.
-   **`r format_number_for_text(adp_presc_latest)`%** of the population being prescribed medication for anxiety, depression, or psychosis. This is a `r adp_presc_diff_scot` proportion than Scotland (`r format_number_for_text(scot_adp_presc)`%).

\newline

### Life Expectancy

`r life_exp_text2`

<!-- <div class = "table-caption-heading">Figure `r figure_num`: Average life expectancy in men and women over time.</div> -->

`r ftext(paste0("Figure ",figure_num,": Average life expectancy in men and women over time"),table_heading_style)`

```{r, fig.width = 8, fig.height = 4.5, fig.cap = 'A line graph showing the trent for average life expectancy in the locality for male and female residents'}
if (LOCALITY %in% check_missing_data_scotpho(life_exp)$area_name) {
  cat("No data available for this locality")
} else {
  life_exp_trend
}

figure_num <- figure_num + 1
```

##### Page break

Table `r table_num` provides the average life expectancy for men and women in different areas for the latest time period available.

<!-- <div custom-style = "table-caption-heading">Table `r table_num`: Average life expectancy in years for the latest time periods (`r latest_period_life_exp_loc` aggregated years for the locality; `r latest_period_life_exp_otherareas` aggregated years for other areas).</div> -->

`r ftext(paste0("Table ",figure_num,": Average life expectancy in years for the latest time periods (",latest_period_life_exp_loc,"aggregated years for the locality; ",latest_period_life_exp_otherareas," aggregated years for other areas)."),table_heading_style)`


```{r}
flextable(life_exp_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  width(width = 6.5 / ncol(life_exp_table))

table_num <- table_num + 1
```

Source: ScotPHO

\newline

`r if(HSCP == "Clackmannanshire and Stirling") {"Note that data is unavailable for Clackmannanshire & Stirling HSCP."}`


### Deaths, aged 15 to 44

The following chart shows a trend of death rates among people aged 15 to 44 per 100,000 age-sex standardised population^4^ by area. In the most recent aggregate time period available (`r latest_period_deaths_15_44`), the mortality rate in `r LOCALITY` locality was **`r format_number_for_text(deaths_15_44_latest)`** deaths per 100,000 population.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Deaths aged 15 to 44 years by geographical area and over time.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Deaths aged 15 to 44 years by geographical area and over time."),table_heading_style)`


```{r, fig.width = 8.5, fig.height = 4.2, fig.cap = 'A line graph showing the ten-year time trend for the 3-year aggregate rate of deaths per 100,000 population for 15 to 44 year olds by locality, HSCP, health board and all Scotland'}
deaths_15_44_time_trend

figure_num <- figure_num + 1
```


Figure `r figure_num` provides comparisons of deaths at ages 15 to 44 across all areas including other localities in `r HSCP` HSCP. In `r latest_period_deaths_15_44`, `r LOCALITY` had a `r deaths_15_44_diff_scot` rate than the rest of Scotland (`r format_number_for_text(deaths_15_44_latest)` compared to `r format_number_for_text(scot_deaths_15_44)` deaths per 100,000).

<!-- <div custom-style = "table-caption-heading">Figure `r figure_num`: Deaths at ages 15 to 44 by area for the latest time period available.</div> -->

`r ftext(paste0("Figure ",figure_num,": Deaths at ages 15 to 44 by area for the latest time period available."),table_heading_style)`


```{r, fig.width = 7.5, fig.height = 4.8, fig.cap = 'A bar graph showing the rate of deaths per 100,000 population for residents aged 15 to 44 by locality, HSCP, health board and all Scotland and for other localitiies in the HSCP between 2019 and 2021.'}
deaths_15_44_bar

figure_num <- figure_num + 1
```


### Long-Term Physical Health Conditions and Multi-morbidity

\newline

In the financial year `r latest_year_ltc`, in `r LOCALITY` Locality, it is estimated that **`r format_number_for_text(ltc_percent_total_latest)`%** of the population had at least one physical long-term condition (LTC). These include cardiovascular, neurodegenerative, and respiratory conditions, as well as other organ conditions (namely liver disease and renal failure), arthritis, cancer, diabetes, and epilepsy. *Please note that estimates for this section are based on people who had contact with NHS services - see footnotes for further information and caveats on identifying LTCs.^5^*

```{r, fig.width = 9, fig.height = 3.5, fig.cap = 'Infographic split by age group showing the number of people out of ten that have at least one LTC. The age groups shown are under 65, 65-74, 75-84, and over 85.'}
ltc_waffles
```

The co-occurrence of two or more conditions, known as multi-morbidity, is broken down in Table `r table_num`, distinguishing between age groups. Overall, **`r format_number_for_text(ltc_multimorbidity_un65_perc)`**% of those under 65 have more than one LTC, compared to **`r format_number_for_text(ltc_multimorbidity_ov65_perc)`**% of those over 65.

<!-- <div custom-style = "table-caption-heading">Table `r table_num`: Multi-morbidity of physical long-term conditions by age group in `r latest_year_ltc`.</div> -->

`r ftext(paste0("Table ",table_num,": Multi-morbidity of physical long-term conditions by age group in",latest_year_ltc),table_heading_style)`


```{r ltc_multimorbidity_table}
flextable(ltc_multimorbidity_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  width(width = 6.5 / ncol(ltc_multimorbidity_table))

table_num <- table_num + 1
```

**Most common physical Long-Term Conditions (LTCs)**

Below is a breakdown of the physical LTCs, for the financial year `r latest_year_ltc`. Figure `r figure_num` shows the prevalence of different LTCs in each age group in `r LOCALITY` locality, and Table `r table_num` illustrates the five most prevalent physical LTCs across all ages at the locality, partnership, and Scotland levels.

<!-- <div custom-style = "table-caption-heading">Figure `r figure_num`: The percentage of people with each physical LTC by age group.</div> -->

`r ftext(paste0("Figure ",figure_num,": The percentage of people with each physical LTC by age group."),table_heading_style)`

```{r, fig.width = 7.5, fig.height = 5, fig.cap = "A graph showing the prevalence of physical long term conditions by percentage of population for Under 65s and for Over 65s."}
ltc_types_plot

figure_num <- figure_num + 1
```

\^\*COPD: Chronic Obstructive Pulmonary Disease\^

<!-- <div custom-style = "table-caption-heading">Table `r table_num`: Prevalence of the five most common physical LTCs as a percentage of the population across geographical areas (1 is the most prevalent).</div> -->

`r ftext(paste0("Table ",table_num,": Prevalence of the five most common physical LTCs as a percentage of the population across geographical areas (1 is the most prevalent)."),table_heading_style)`


```{r, fig.width = 7.5, fig.height = 3.5}
top5_ltc_table

table_num <- table_num + 1
```

Source: Source Linkage Files

### Cancer

For the period `r latest_period_cancer_reg`, there were **`r format_number_for_text(cancer_reg_total_latest)`** new cancer registrations per year on average (a rate of **`r format_number_for_text(cancer_reg_rate_latest)`** registrations per 100,000 age-sex standardised population) in `r LOCALITY` locality. For the period `r latest_period_early_deaths_cancer`, there were also **`r format_number_for_text(early_deaths_cancer_rate_latest)`** early deaths per 100,000 from cancer in the locality, this is a **`r format_number_for_text(cancer_deaths_perc_change)`%** `r cancer_deaths_changeword` compared to the rate 10 years prior.

<!-- <div custom-style = "table-caption-heading">Figure `r figure_num`: Cancer registration rate over time and by area.</div> -->

`r ftext(paste0("Figure ",figure_num,": Cancer registration rate over time and by area."),table_heading_style)`

```{r, fig.width = 8.5, fig.height = 3.7, fig.cap = "A line graph showing 10-year time trends for cancer registrations per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
cancer_reg_time_trend

figure_num <- figure_num + 1
```

<!-- <div custom-style = "table-caption-heading">Figure `r figure_num`: Early deaths from cancer (\<75 years) over time and by area.</div> -->

`r ftext(paste0("Figure ",figure_num,": Early deaths from cancer (<75 years) over time and by area."),table_heading_style)`


```{r, fig.width = 8.5, fig.height = 3.7, fig.cap = "A line graph showing 10-year time trends for early deaths from cancer per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
early_deaths_cancer_time_trend

figure_num <- figure_num + 1
```


### Hospitalisations by condition

Patient hospitalisations can indicate how certain diseases have varying impacts on people's lives. In the latest time period available in `r LOCALITY`, the condition with the highest rate of hospitalisations was `r highest_hosp_disease$indicator`.

<!-- <div custom-style = "table-caption-heading">Table `r table_num`: Patient hospitalisations by condition and geographical area, age-sex standardised rates per 100,000.</div> -->

`r ftext(paste0("Table ",table_num,": Patient hospitalisations by condition and geographical area, age-sex standardised rates per 100,000."),table_heading_style)`


```{r disease_hosp_table}
flextable(disease_hosp_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  width(width = 6.5 / ncol(disease_hosp_table)) |>
  set_table_properties(layout = "autofit", width = 1)

table_num <- table_num + 1
```


### Anxiety, Depression and Psychosis (ADP) prescriptions

In `r latest_period_adp_presc`, **`r format_number_for_text(adp_presc_latest)`%** of people were prescribed medication for anxiety, depression or psychosis in `r LOCALITY` Locality. This is a **`r format_number_for_text(adp_presc_perc_change)`% `r adp_presc_changeword`** from the rate 10 years prior in `r prev_period_adp_presc` which was `r format_number_for_text(adp_presc_earliest)`%.

<!-- <div custom-style = "table-caption-heading">Figure `r figure_num`: Anxiety, depression and psychosis prescriptions over time and by geographical area.</div> -->

`r ftext(paste0("Figure ",figure_num,": Anxiety, depression and psychosis prescriptions over time and by geographical area."),table_heading_style)`


```{r, fig.width = 8.5, fig.height = 3.8, fig.cap = "A line graph showing 10-year time trends for anxiety, depression and psychosis prescriptions by percentage of population for Locality, HSCP, Health Board and all Scotland."}
adp_presc_time_trend

figure_num <- figure_num + 1
```


In `r latest_period_adp_presc`, `r LOCALITY` had a `r adp_presc_diff_scot` proportion of the population being prescribed ADP medication compared to the rest of Scotland (`r format_number_for_text(adp_presc_latest)`% compared to `r format_number_for_text(scot_adp_presc)`%).

<!-- <div custom-style = "table-caption-heading">Figure `r figure_num`: Percentage population prescribed medication for anxiety, depression and psychosis by area for the latest period available.</div> -->

`r ftext(paste0("Figure ",figure_num,": Percentage population prescribed medication for anxiety, depression and psychosis by area for the latest period available."),table_heading_style)`


```{r, fig.width = 7.5, fig.height = 4.8, fig.cap = "A bar graph showing the percentage of the population prescribed anxiety, depression and psychosis medication in the most recent financial year for all Localities in the partnership and the total percentage for the HSCP, Health Board and all Scotland."}
adp_presc_bar

figure_num <- figure_num + 1
```

<!--chapter:end:General-Health.Rmd-->


\newpage

# Lifestyle and Risk Factors

\newline

**Summary**

Mental and physical well-being has close ties with people's lifestyles and behaviours. Financial security, employment and location are influences that often have a bearing on these choices. Issues can develop when alcohol, smoking or drug use shape lives. This section provides data on drug-related hospital admissions, alcohol-related hospital admissions, alcohol-specific deaths and bowel screening uptake, to give an overview of some of the lifestyles and behaviours for the `r LOCALITY` locality. These can give an idea of quality of life and prosperity.

For the most recent time period available^3^, `r LOCALITY` had:

-   **`r format_number_for_text(alcohol_hosp_latest)`** alcohol-related hospital admissions per 100,000 age-sex standardised population. This is `r alcohol_hosp_diff_scot` than Scotland (`r  format_number_for_text(scot_alcohol_hosp)` admissions per 100,000)^4^.
-   **`r format_number_for_text(alcohol_deaths_latest)`** alcohol-specific deaths per 100,000 age-sex standardised population. This is `r alcohol_deaths_diff_scot` than Scotland (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000)^4^.
-   **`r format_number_for_text(drug_hosp_latest)`** drug-related hospital admissions per 100,000 age-sex standardised population. This is `r drug_hosp_diff_scot` than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000)^4^.
-   **`r format_number_for_text(bowel_screening_latest)`%** uptake of bowel screening among the eligible population, compared to `r format_number_for_text(scot_bowel_screening)`% in Scotland.

\newline

### Alcohol-related Hospital Admissions

In `r latest_period_alcohol_hosp`, the rate of alcohol-related admissions was **`r format_number_for_text(alcohol_hosp_latest)`** per 100,000 age-sex standardised population in `r LOCALITY`. This is `r get_article(alcohol_hosp_change)` `r format_number_for_text(alcohol_hosp_change)`% `r alcohol_hosp_change_word` overall since `r earliest_period_alcohol_hosp`. Figure `r figure_num` shows a trend of alcohol-related hospital admissions for `r LOCALITY` locality compared with Scotland, `r HSCP` HSCP and `r HB` from financial year `r earliest_period_alcohol_hosp` to `r latest_period_alcohol_hosp`.

Figure `r figure_num + 1` then compares different areas, including the other localities in `r HSCP`, for the latest financial year. This bar chart shows that in `r latest_period_alcohol_hosp`, `r LOCALITY` locality had a `r alcohol_hosp_diff_scot` alcohol-related hospital admissions rate compared to Scotland (`r format_number_for_text(alcohol_hosp_latest)` and `r  format_number_for_text(scot_alcohol_hosp)` admissions respectively).


<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Alcohol-related hospital admission rates by area and over time.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Alcohol-related hospital admission rates by area and over time."),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing 10-year time trends for alcohol-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
alcohol_hosp_time_trend

figure_num <- figure_num + 1
```

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Alcohol-related hospital admissions by area for the latest time period.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Alcohol-related hospital admissions by area for the latest time period."),table_heading_style)`

```{r fig.width = 7.5, fig.height = 4.8, warning = FALSE, fig.cap = "A bar graph showing alcohol-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent financial year."}
alcohol_hosp_bar

figure_num <- figure_num + 1
```

\newline

### Alcohol-Specific Deaths

Data on alcohol-specific deaths is available as 5-year aggregates. In `r LOCALITY`, the latest rate of alcohol-specific deaths was **`r format_number_for_text(alcohol_deaths_latest)`** deaths per 100,000 age-sex standardised population. This is `r format_number_for_text(alcohol_deaths_change)`% `r alcohol_deaths_change_word` than the rate in `r earliest_period_alcohol_deaths`. Figure `r figure_num + 1` also shows that the locality has a `r alcohol_deaths_diff_scot` alcohol-specific death rate compared to Scotland overall (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000).

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Alcohol-specific deaths by area and over time.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Alcohol-specific deaths by area and over time."),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing 10-year time trends for 5 year aggregate rates of alcohol-specific deaths per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
alcohol_deaths_time_trend

figure_num <- figure_num + 1
```

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Alcohol-specific deaths by area for the latest time period available.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Alcohol-specific deaths by area for the latest time period available."),table_heading_style)`

```{r fig.width = 7.5, fig.height = 4.5, warning = FALSE, fig.cap =  "A bar graph showing the 5 year aggregate rate of alcohol-specific deaths per 100,000 population for Locality, HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent time period."}
alcohol_deaths_bar

figure_num <- figure_num + 1
```


### Drug-related Hospital Admissions

There were **`r format_number_for_text(drug_hosp_latest)`** drug-related hospital admissions per 100,000 age-sex standardised population^4^ in the `r LOCALITY` locality in the time period `r latest_period_drug_hosp` (3-year financial year aggregate). This is `r get_article(drug_hosp_change)` `r format_number_for_text(drug_hosp_change)`% `r drug_hosp_change_word` since `r earliest_period_drug_hosp`. A trend of the change in drug-related hospital admissions for the locality and comparable areas is shown in Figure `r figure_num` from `r earliest_period_drug_hosp_trend` onward.

A comparison of areas at the most recent time period (`r latest_period_drug_hosp` aggregated financial years) is available in Figure `r figure_num + 1` This shows the `r LOCALITY` locality has a `r drug_hosp_diff_scot` rate of drug-related hospital admissions than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000).

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Drug-related hospital admission rates by area and over time.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Drug-related hospital admission rates by area and over time."),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing time trends for 3 year aggregate rates of drug-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
drug_hosp_time_trend

figure_num <- figure_num + 1
```

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Drug-related hospital admission rates by area for the latest time period available.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Drug-related hospital admission rates by area for the latest time period available."),table_heading_style)`

```{r fig.width = 8, fig.height = 4.8, warning = FALSE, fig.cap= "A bar graph showing the 3 year rate of drug-related hospital admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent time period."}
drug_hosp_bar

figure_num <- figure_num + 1
```

\newline

### Bowel Screening Uptake

Bowel screening is offered every two years to eligible men and women aged between 50-74 years old. Eligible people are posted a test kit which is completed at home. Since 1st April 2013, those aged 75 and over can also self-refer and opt into screening.

A trend of the percentage uptake of bowel screening among the eligible population is shown for `r LOCALITY` and comparable areas. Data is presented as 3-year aggregates. The `r latest_period_bowel_screening` uptake rate for `r LOCALITY` is **`r format_number_for_text(bowel_screening_latest)`%**. This is `r get_article(bowel_screening_change)` `r format_number_for_text(bowel_screening_change)`% `r bowel_screening_change_word` since `r earliest_period_bowel_screening`. As can be seen in Figure `r figure_num + 1`, in the latest estimate, the uptake in `r LOCALITY` was `r bowel_screening_diff_scot` than the uptake in Scotland overall (`r format_number_for_text(scot_bowel_screening)`%).

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Bowel screening uptake for eligible men and women, by area and over time.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Bowel screening uptake for eligible men and women, by area and over time."),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing time trends for 3 year aggregate rates for bowel screening uptake by percentage of eligible population for Locality, HSCP, Health Board and all Scotland."}
bowel_screening_time_trend

figure_num <- figure_num + 1
```

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Bowel screening uptake by area for the latest time period available.</Div> -->

`r ftext(paste0("Figure ",figure_num,": Bowel screening uptake by area for the latest time period available."),table_heading_style)`

```{r fig.width = 7.5, fig.height = 4.8, warning = FALSE, fig.cap = "A bar graph showing the most recent 3 year aggregate rates for bowel screening uptake by percentage of eligible population for Locality, HSCP, Health Board and all Scotland and for all localities within the HSCP."}
bowel_screening_bar

figure_num <- figure_num + 1
```

<!--chapter:end:Lifestyle-Risk-Factors.Rmd-->


\newpage

# Hospital and Community Care

\newline

**Summary**

**For the most recent time periods available, `r LOCALITY` had:**

-   **`r latest_emergency_adm_loc1`** emergency hospital admissions per 100,000 population, compared to `r scot_emergency_adm1` in Scotland.

-   **`r latest_bed_days_loc1`** unscheduled acute specialty bed days per 100,000 population, compared to `r scot_bed_days1` in Scotland.

-   **`r latest_ae_att_loc1`** A&E attendances per 100,000 population, compared to `r scot_ae_att1` in Scotland.

-   **`r latest_dd_loc1`** delayed discharge bed days per 100,000 population aged over 65, compared to `r scot_dd1` in Scotland.

-   **`r latest_falls_loc1`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r scot_falls1` in Scotland.

-   **`r latest_read_loc1`** emergency readmissions (28 day) per 1,000 discharges, compared to `r scot_read` in Scotland.

-   **`r latest_ppa_loc$formatted_data[2]`** potentially preventable hospital admissions per 100,000 population, compared to `r scot_ppa$formatted_data[2]` in Scotland.

### Emergency Admissions

Figure `r figure_num` presents the emergency admissions rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ea` to `r max_year_ea`.

As presented in Figure `r figure_num`, the emergency admissions rate in the `r LOCALITY` locality for `r max_year_ea` is `r latest_emergency_adm_loc1`, `r get_article(percent_rate_change)` `r percent_rate_change`% `r word_change_rate` since `r min_year_ea`. The `r HSCP` HSCP rate is `r hscp_emergency_adm1`, `r get_article(hscp_rate_change)` `r hscp_rate_change`% `r word_change_hscp` since `r min_year_ea`. The `r HB` health board rate is `r hb_emergency_adm1` in `r max_year_ea`, `r get_article(hb_rate_change)` `r hb_rate_change`% `r word_change_hb` since `r min_year_ea` and the Scotland rate is `r scot_emergency_adm1`, `r get_article(scot_rate_change)` `r scot_rate_change`% `r word_change_scot` since `r min_year_ea`.


<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Emergency admissions by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Emergency admissions by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
EAs_loc_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` presents the emergency admissions rate per 100,000 population in the `r LOCALITY` locality from `r min_ea_age` to `r max_ea_age` by age group.

As presented in Figure `r figure_num`, the highest emergency admissions rate for the `r LOCALITY` locality in `r max_ea_age` is `r latest_ea_max_age1` per 100,000 population for the `r age_group_max_ea` age group with a percentage `r max_word_change_ea` of `r max_rate_change_ea`% since `r min_ea_age`. The lowest emergency admissions rate for `r LOCALITY` in `r max_ea_age` is `r latest_ea_min_age1` per 100,000 population for the `r age_group_min_ea` age group with a percentage `r min_word_change_ea` of `r min_rate_change_ea`% since `r min_ea_age`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Emergency admissions by age group</Div> -->

`r ftext(paste0("Figure ",figure_num,": Emergency admissions by age group"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE,  fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
EAs_age_ts

figure_num <- figure_num + 1
```

### Unscheduled Acute Bed Days

Figure `r figure_num` presents the unscheduled bed days rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ubd` to `r max_year_ubd`.

As presented in Figure `r figure_num`, the unscheduled bed days rate in the `r LOCALITY` locality for `r max_year_ubd` is `r latest_bed_days_loc1`, `r get_article(rate_change_ubd)` `r rate_change_ubd`% `r word_change_ubd` since `r min_year_ubd` and the `r HSCP` HSCP rate is `r hscp_bed_days1`, `r get_article(hscp_rate_ubd)` `r hscp_rate_ubd`% `r hscp_change_ubd` since `r min_year_ubd`. The `r HB` health board rate for `r max_year_ubd` is `r hb_bed_days1`, `r get_article(hb_rate_change_ubd)` `r hb_rate_change_ubd`% `r word_change_hb_ubd` since `r min_year_ubd` and the Scotland rate is `r scot_bed_days1`, `r get_article(scot_rate_ubd)` `r scot_rate_ubd`% `r scot_change_ubd` since `r min_year_ubd`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Unscheduled acute bed days by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Unscheduled acute bed days by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for unscheduled acute bed days per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
BDs_loc_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` presents the unscheduled bed days rate per 100,000 population in the `r LOCALITY` locality from `r min_ubd_age` to `r max_ubd_age` by age group.

As presented in Figure `r figure_num`, the highest unscheduled bed days rate for the `r LOCALITY` locality in `r max_ubd_age` is `r latest_ubd_max_age1` bed days per 100,000 population for the `r age_group_max_ubd` age group with a percentage `r max_word_change_ubd` of `r max_rate_change_ubd`% since `r min_ubd_age`. The lowest unscheduled bed days rate for `r LOCALITY` in `r max_ubd_age` is `r latest_ubd_min_age1` bed days per 100,000 population for the `r age_group_min_ubd` age group with a percentage `r min_word_change_ubd` of `r min_rate_change_ubd`% since `r min_ubd_age`.


<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Unscheduled acute bed days by age group</Div> -->

`r ftext(paste0("Figure ",figure_num,": Unscheduled acute bed days by age group"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
BDs_age_ts

figure_num <- figure_num + 1
```


### A&E Attendances

Figure `r figure_num` presents the A&E attendance rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ae_area` to `r max_year_ae_area`.

As presented in Figure `r figure_num`, the A&E attendance rate per 100,000 in the `r LOCALITY` locality for `r max_year_ae_area` is `r latest_ae_att_loc1`, `r get_article(percent_rate_change_ae_areas)` `r percent_rate_change_ae_areas`% `r word_change_rate_ae_areas` since `r min_year_ae_area` and the `r HSCP` HSCP rate is `r hscp_ae_att1`, `r get_article(percent_rate_change_ae_areas_hscp)` `r percent_rate_change_ae_areas_hscp`% `r word_change_rate_ae_areas_hscp` since `r min_year_ae_area`. The `r HB` health board rate for `r max_year_ae_area` is `r hb_ae1`, `r get_article(hb_rate_change_ae)` `r hb_rate_change_ae`% `r word_change_hb_ae` since `r min_year_ae_area` and the Scotland rate is `r scot_ae_att1`, `r get_article(percent_rate_change_ae_areas_scot)` `r percent_rate_change_ae_areas_scot`% `r word_change_rate_ae_areas_scot` since `r min_year_ae_area`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: A&E attendances by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": A&E attendances by geographical area"),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
AandE_loc_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` presents the A&E attendance rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ae_area` to `r max_year_ae_area` by age group.

As presented in Figure `r figure_num`, the highest A&E attendance rate for the `r LOCALITY` locality in `r max_year_ae_age` is `r latest_ae_att_loc1_age` per 100,000 population for the `r age_group_max` age group with a percentage `r word_change_rate_ae_age` of `r percent_rate_change_ae_age`% since `r min_year_ae_age`. The lowest A&E attendance rate for `r LOCALITY` in `r max_year_ae_age` is `r latest_ae_att_loc1_age_min` per 100,000 population for the `r age_group_min` age group with a percentage `r word_change_rate_ae_age2` of `r percent_rate_change_ae_age2`% since `r min_year_ae_age`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: A&E attendances by age group</Div> -->

`r ftext(paste0("Figure ",figure_num,": A&E attendances by age group"),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population split by age group."}
AandE_age_ts

figure_num <- figure_num + 1
```


### Emergency Readmissions (28 days)

Figure `r figure_num` presents the emergency readmission (28 days) rate per 1,000 discharges in the `r LOCALITY` locality from `r min_year_re_area` to `r max_year_re_area`.

As presented in Figure `r figure_num`, the emergency readmission (28 days) rate per 1,000 discharges in the `r LOCALITY` locality for `r max_year_re_area` is `r latest_read_loc1`, `r get_article(percent_rate_change_re_area)` `r percent_rate_change_re_area`% `r word_change_rate_re_area` since `r min_year_re_area` and the `r HSCP` HSCP rate is `r hscp_read`, `r get_article(percent_rate_change_re_area_hscp)` `r percent_rate_change_re_area_hscp`% `r word_change_rate_re_area_hscp` since `r min_year_re_area`. The `r HB` health board rate for `r max_year_re_area` is `r hb_read1`, `r get_article(hb_rate_change_read)` `r hb_rate_change_read`% `r word_change_hb_read` since `r min_year_re_area` and the Scotland rate is `r scot_read`, `r get_article(percent_rate_change_re_area_scot)` `r percent_rate_change_re_area_scot`% `r word_change_rate_re_area_scot` since `r min_year_re_area`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Emergency readmissions (28 days) by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Emergency readmissions (28 days) by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by geographical area."}
read_loc_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` presents the emergency readmission (28 days) rate per 1,000 discharges in the `r LOCALITY` locality from `r min_year_re_age` to `r max_year_re_age` by age group.

As presented in Figure `r figure_num`, the highest emergency readmission (28 days) rate for the `r LOCALITY` locality in `r max_year_re_age` is `r latest_re_max_age_data` per 1,000 discharges for the `r latest_re_max_age_group` age group with a percentage `r word_change_rate_re_age` of `r percent_rate_change_re_age`% since `r min_year_re_age`. The lowest emergency readmission (28 days) rate for the `r LOCALITY` locality in `r max_year_re_age` is `r latest_re_min_age_data` per 1,000 discharges for the `r latest_re_min_age_group` age group with a percentage `r word_change_rate_re_age_min` of `r percent_rate_change_re_age_min`% since `r min_year_re_age`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Emergency readmissions (28 days) by age group</Div> -->

`r ftext(paste0("Figure ",figure_num,": Emergency readmissions (28 days) by age group"),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by age group."}
read_age_ts

figure_num <- figure_num + 1
```


### Delayed Discharge Bed Days

Figure `r figure_num` presents the number of delayed discharge bed days per 100,000 population aged over 65+ in the `r LOCALITY` locality from `r min_year_dd` to `r max_year_dd`.

As presented in Figure `r figure_num`, the number of delayed discharge bed days per 100,000 population aged over 65+ in the `r LOCALITY` locality for `r max_year_dd` is `r latest_dd_loc1`, `r get_article(percent_rate_change_dd_loc)` `r percent_rate_change_dd_loc`% `r word_change_rate_dd_loc` since `r min_year_dd` and the `r HSCP` HSCP rate is `r hscp_dd1`, `r get_article(percent_rate_change_dd_hscp)` `r percent_rate_change_dd_hscp`% `r word_change_rate_dd_hscp` since `r min_year_dd`. The `r HB` health board rate for `r max_year_dd` is `r hb_dd1`, `r get_article(hb_rate_change_dd)` `r hb_rate_change_dd`% `r word_change_hb_dd` since `r min_year_dd` and the Scotland rate is `r scot_dd1`, `r get_article(percent_rate_change_dd_scot)` `r percent_rate_change_dd_scot`% `r  word_change_rate_dd_scot` since `r min_year_dd`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Delayed discharge bed days in the population aged 65+ by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Delayed discharge bed days in the population aged 65+ by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for delayed discharge beddays per 100,000 population aged 65+ split by geographical area."}
DD_loc_ts

figure_num <- figure_num + 1
```

### Emergency admissions from a fall

Figure `r figure_num` presents the emergency admissions from falls rate per 100,000 population aged 65 and over in the `r LOCALITY` locality from `r min_year_falls` to `r max_year_falls`.

As presented in Figure `r figure_num`, the emergency admissions from falls rate per 100,000 population aged over 65+ in the `r LOCALITY` locality for `r max_year_falls` is `r latest_falls_loc1`, `r get_article(percent_rate_change_falls_loc)` `r percent_rate_change_falls_loc`% `r word_change_rate_falls_loc` since `r min_year_falls` and the `r HSCP` HSCP rate is `r hscp_falls1`, `r get_article(percent_rate_change_falls_hscp)` `r percent_rate_change_falls_hscp`% `r word_change_rate_falls_hscp` since `r min_year_falls`. The `r HB` health board rate for `r max_year_falls` is `r hb_falls1`, `r get_article(hb_rate_change_falls)` `r hb_rate_change_falls`% `r word_change_hb_falls` since `r min_year_falls` and the Scotland rate is `r scot_falls1`, `r get_article(percent_rate_change_falls_scot)` `r percent_rate_change_falls_scot`% `r  word_change_rate_falls_scot` since `r min_year_falls`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Falls in the population aged 65+ by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Falls in the population aged 65+ by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency admissions from a fall per 100,000 population aged 65+ split by geographical area."}
Falls_loc_ts

figure_num <- figure_num + 1
```


### Potentially Preventable Admissions (PPAs)

Information on the conditions included in Potentially Preventable Admissions (PPA)s is available in Appendix 3. In `r max_fy`, **`r latest_ppa_65plus`%** of PPAs in `r LOCALITY` were amongst those aged 65 and over, and **`r latest_ppa_under65`%** were amongst those aged under 65.

Figure `r figure_num` presents the PPA rate per 100,000 population in the `r LOCALITY` locality from `r min_year_ppa_areas` to `r max_year_ppa_areas`. The rate per 100,000 population for PPAs in the `r LOCALITY` locality for `r max_year_ppa_areas` is `r latest_ppa_loc$formatted_data[2]`, `r get_article(ppa_diff)` `r ppa_diff`% `r ppa_word_change` since `r latest_ppa_loc$financial_year[1]` and the `r HSCP` HSCP rate is `r hscp_ppa$data[2]`, `r get_article(ppa_diff_hscp)` `r ppa_diff_hscp`% `r ppa_word_change_hscp` since `r latest_ppa_loc$financial_year[1]`. The `r HB` health board rate for `r hb_ppa$financial_year[2]` is `r hb_ppa$formatted_data[2]`, `r get_article(diff_hb_ppa)` `r diff_hb_ppa`% `r word_change_hb_ppa` since `r hb_ppa$financial_year[]` and the Scotland rate is `r scot_ppa$formatted_data[2]`, `r get_article(diff_scot_ppa)` `r diff_scot_ppa`% `r  word_change_scot_ppa` since `r hb_ppa$financial_year[1]`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Potentially Preventable Admissions (PPAs) by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Potentially Preventable Admissions (PPAs) by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for potentially preventable admissions per 100,000 population split by geographical area."}
ppa_loc_ts

figure_num <- figure_num + 1
```

\newpage

## Hospital Care (Mental Health Speciality)

\newline

**Summary**

This section looks at mental health-related unscheduled care indicators. For the most recent time period available, `r LOCALITY` had:

-   **`r psych_hosp_latest`** psychiatric patient hospitalisations per 100,000, compared to `r scot_psych_hosp$measure[2]` in Scotland^4^.
-   **`r latest_bed_days_mh_loc1`** unscheduled mental health specialty bed days per 100,000, compared to `r scot_bed_days_mh1` in Scotland.

\newline

### Psychiatric patient hospitalisations

Figure `r figure_num` presents the psychiatric patient hospitalisation 3-year aggregate rate per 100,000 population in the `r LOCALITY` locality from `r loc_psych_hosp$period_short[1]` to `r loc_psych_hosp$period_short[2]`.

As presented in Figure `r figure_num`, the 3-year aggregate psychiatric patient hospitalisation rate per 100,000 population in the `r LOCALITY` locality for `r loc_psych_hosp$period_short[2]` is `r loc_psych_hosp$measure[2]`, `r get_article(diff_loc_psych)` `r diff_loc_psych`% `r word_change_loc_psych` since `r loc_psych_hosp$period_short[1]` and the `r HSCP` HSCP rate is `r hscp_psych_hosp$measure[2]`, `r get_article(diff_hscp_psych)` `r diff_hscp_psych`% `r word_change_hscp_psych` since `r loc_psych_hosp$period_short[1]`. The `r HB` health board the 3-year aggregate rate for `r loc_psych_hosp$period_short[2]` is `r hb_psych_hosp$measure[2]`, `r get_article(diff_hb_psych)` `r diff_hb_psych`% `r word_change_hb_psych` since `r loc_psych_hosp$period_short[1]` and the Scotland the 3-year aggregate rate is `r scot_psych_hosp$measure[2]`, `r get_article(diff_scot_psych)` `r diff_scot_psych`% `r word_change_scot_psych` since `r loc_psych_hosp$period_short[1]`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Psychiatric patient hospitalisations by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Psychiatric patient hospitalisations by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing ten-year time trends grouped into 3 year aggregates for psychiatric patient hospitalisations per 100,000 population split by geographical area."}
psych_hosp_time_trend

figure_num <- figure_num + 1
```


### Unscheduled Mental Health Specialty Bed Days

Figure `r figure_num` presents the unscheduled mental health bed days rate per 100,000 population in the `r LOCALITY` locality from `r min_year_bd_mh_areas` to `r max_year_bd_mh_areas`.

As presented in Figure `r figure_num`, the unscheduled mental health bed days rate per 100,000 population in the `r LOCALITY` locality for `r max_year_bd_mh_areas` is `r latest_bed_days_mh_loc1`, `r get_article(loc_rate_change_beds_mh)` `r loc_rate_change_beds_mh`% `r loc_word_change_beds_mh` since `r min_year_bd_mh_areas` and the `r HSCP` HSCP rate is `r hscp_bed_days_mh1`, `r get_article(hscp_rate_change_beds_mh)` `r hscp_rate_change_beds_mh`% `r hscp_word_change_beds_mh` since `r min_year_bd_mh_areas`. The `r HB` health board rate for `r max_year_bd_mh_areas` is `r hb_mh_beddays1`, `r get_article(hb_rate_change_mh)` `r hb_rate_change_mh`% `r word_change_hb_mh` since `r  min_year_bd_mh_areas` and the Scotland rate is `r scot_bed_days_mh1`, `r get_article(scot_rate_change_beds_mh)` `r scot_rate_change_beds_mh`% `r  scot_word_change_beds_mh` since `r min_year_bd_mh_areas`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Unscheduled mental health specialty bed days by geographical area</Div> -->

`r ftext(paste0("Figure ",figure_num,": Unscheduled mental health specialty bed days by geographical area"),table_heading_style)`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_loc_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` presents the unscheduled mental health bed days rate per 100,000 in the `r LOCALITY` locality from `r min_year_bd_mh_age` to `r max_year_bd_mh_age` by age group.

As presented in Figure `r figure_num`, the highest unscheduled mental health bed days rate for the `r LOCALITY` locality in `r max_year_bd_mh_age` is `r latest_bd_mh_max_age1` per 100,000 population for the `r age_group_max_mh` age group with a percentage `r max_word_change_beds_mh` of `r max_rate_change_beds_mh`% since `r min_year_bd_mh_age`. The lowest unscheduled mental health bed days rate for the `r LOCALITY` locality in `r max_year_bd_mh_age` is `r latest_bd_mh_min_age1` per 100,000 population for the `r age_group_min_mh` age group with a percentage `r min_word_change_beds_mh` of `r min_rate_change_beds_mh`% since `r min_year_bd_mh_age1`.

<!-- <Div custom-style = "Table or chart caption">Figure `r figure_num`: Unscheduled mental health specialty bed days by age group</Div> -->

`r ftext(paste0("Figure ",figure_num,": Unscheduled mental health specialty bed days by age group"),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_age_ts

figure_num <- figure_num + 1
```

<!--chapter:end:Unscheduled-Care.Rmd-->

