\newpage

# General Health

## Summary

For the most recent time period available^4^, `r HSCP` HSCP had:

```{r life_exp_text}
if (is.na(avg_life_exp_latest_male)) {
  life_exp_text <- "No data available for life expectancy."
  life_exp_text2 <- "No data available for life expectancy at locality level."
} else {
  life_exp_text <- glue("An average life expectancy of **{avg_life_exp_latest_male}** years for males and **{avg_life_exp_latest_fem}** years for females, compared to the national average of {scot_life_exp_male} and {scot_life_exp_fem} years of age respectively.")
  life_exp_text2 <- glue("In the latest time period available from {latest_period_life_exp_loc} (3-year aggregate), the average life expectancy in {HSCP} HSCP was {avg_life_exp_latest_male} years for men, and {avg_life_exp_latest_fem} years for women. A 10-year time trend can be seen in figure {figure_num}.")
}
```

-   `r life_exp_text`
-   A death rate for ages 15 to 44 of **`r format_number_for_text(deaths_15_44_latest)`** deaths per 100,000 age-sex standardised population. This is `r deaths_15_44_diff_scot` than Scotland (`r format_number_for_text(scot_deaths_15_44)` deaths per 100,000)^4^.
-   **`r format_number_for_text(ltc_percent_total_latest)`%** of the HSCP's population with at least one long-term physical health condition. This is `r ltc_diff_scot` than Scotland (`r format_number_for_text(ltc_perc_scot)`%).
-   A cancer registration rate of **`r format_number_for_text(cancer_reg_rate_latest)`** registrations per 100,000 age-sex standardised population (compared to `r format_number_for_text(scot_cancer)` in Scotland), and an early death rate (\<75 years) from cancer of **`r format_number_for_text(early_deaths_cancer_rate_latest)`** per 100,000 age-sex standardised population (compared to `r format_number_for_text(scot_cancer_deaths)` in Scotland)^4^.
-   **`r format_number_for_text(adp_presc_latest)`%** of the population being prescribed medication for anxiety, depression, or psychosis. This is a `r adp_presc_diff_scot` proportion than Scotland (`r format_number_for_text(scot_adp_presc)`%).

## Life Expectancy

`r life_exp_text2`

```{r, fig.width = 8, fig.height = 4.5, fig.cap = 'A line graph showing the trent for average life expectancy in the locality for male and female residents'}
ftext(paste0("Figure ", figure_num, ": Average life expectancy in men and women over time"), table_heading_style)

if (HSCP %in% check_missing_data_scotpho(life_exp)$area_name) {
  cat("No data available for this HSCP")
} else {
  life_exp_trend
}

figure_num <- figure_num + 1
```

Table `r table_num` provides the average life expectancy for men and women in different areas for the latest time period available.

```{r}
ftext(
  glue("Table {figure_num}: Average life expectancy in years for the latest time periods ({latest_period_life_exp_loc} aggregated years for the HSCP; {latest_period_life_exp_otherareas} aggregated years for other areas)."),
  table_heading_style
)

flextable(life_exp_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  width(width = 6.5 / ncol(life_exp_table))

table_num <- table_num + 1
```

Source: ScotPHO

`r if(HSCP == "Clackmannanshire and Stirling") {"Note that data is unavailable for Clackmannanshire & Stirling HSCP."}`

## Deaths, aged 15 to 44

The following chart shows a trend of death rates among people aged 15 to 44 per 100,000 age-sex standardised population^4^ by area. In the most recent aggregate time period available (`r latest_period_deaths_15_44`), the mortality rate in `r HSCP` HSCP was **`r format_number_for_text(deaths_15_44_latest)`** deaths per 100,000 population.

```{r, fig.width = 8.5, fig.height = 4.2, fig.cap = 'A line graph showing the ten-year time trend for the 3-year aggregate rate of deaths per 100,000 population for 15 to 44 year olds by locality, HSCP, health board and all Scotland'}
ftext(paste0("Figure ", figure_num, ": Deaths aged 15 to 44 years by geographical area and over time."), table_heading_style)

deaths_15_44_time_trend

figure_num <- figure_num + 1
```

Figure `r figure_num` provides comparisons of deaths at ages 15 to 44 across all areas including other localities in `r HSCP` HSCP. In `r latest_period_deaths_15_44`, `r HSCP` had a `r deaths_15_44_diff_scot` rate than the rest of Scotland (`r format_number_for_text(deaths_15_44_latest)` compared to `r format_number_for_text(scot_deaths_15_44)` deaths per 100,000).

```{r, fig.width = 7.5, fig.height = 4.8, fig.cap = 'A bar graph showing the rate of deaths per 100,000 population for residents aged 15 to 44 by locality, HSCP, health board and all Scotland and for other localitiies in the HSCP between 2019 and 2021.'}
ftext(paste0("Figure ", figure_num, ": Deaths at ages 15 to 44 by area for the latest time period available."), table_heading_style)

deaths_15_44_bar

figure_num <- figure_num + 1
```

## Long-Term Physical Health Conditions and Multi-morbidity

The estimates in the following sections are based on an individual being hospitalised with a relevant condition *at any point* in the past. This methodology can lead to both undercounts and overcounts depending on the condition; see the footnotes for more details.^5^

In the financial year `r latest_year_ltc`, in `r HSCP` HSCP, it is estimated that **`r format_number_for_text(ltc_percent_total_latest)`%** of the population had at least one physical long-term condition (LTC). These include cardiovascular, neurodegenerative, and respiratory conditions, as well as other organ conditions (namely liver disease and renal failure), arthritis, cancer, diabetes, and epilepsy. *Please note that estimates for this section are based on people who had contact with NHS services - see footnotes for further information and caveats on identifying LTCs.^6^*

```{r, fig.width = 9, fig.height = 3.5, fig.cap = 'Infographic split by age group showing the number of people out of ten that have at least one LTC. The age groups shown are under 65, 65-74, 75-84, and over 85.'}
ltc_waffles
```

The co-occurrence of two or more conditions, known as multi-morbidity, is broken down in Table `r table_num`, distinguishing between age groups. Overall, **`r format_number_for_text(ltc_multimorbidity_un65_perc)`**% of those under 65 have more than one LTC, compared to **`r format_number_for_text(ltc_multimorbidity_ov65_perc)`**% of those over 65.

```{r ltc_multimorbidity_table}
ftext(paste0("Table ", table_num, ": Multi-morbidity of physical long-term conditions by age group in", latest_year_ltc), table_heading_style)

flextable(ltc_multimorbidity_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  width(width = 6.5 / ncol(ltc_multimorbidity_table))

table_num <- table_num + 1
```

**Most common physical Long-Term Conditions (LTCs)**

-   Figure `r figure_num` shows the Long-Term condition prevalence estimates for `r HSCP` HSCP in the financial year `r latest_year_ltc` for under 65s and over 65s.

-   Table `r table_num` orders the prevalance estimates to show the most common five physical LTCs across all ages at the locality, partnership, and Scotland levels.

Below is a breakdown of the physical LTCs, for the financial year `r latest_year_ltc`. Figure `r figure_num` shows the prevalence of different LTCs in each age group in `r HSCP` HSCP, and Table `r table_num` illustrates the five most prevalent physical LTCs across all ages at the partnership, and Scotland levels.

```{r, fig.width = 7.5, fig.height = 5, fig.cap = "A graph showing the prevalence of physical long term conditions by percentage of population for Under 65s and for Over 65s."}
ftext(paste0("Figure ", figure_num, ": The percentage of people with each physical LTC by age group."), table_heading_style)

ltc_types_plot

figure_num <- figure_num + 1

ftext("*COPD: Chronic Obstructive Pulmonary Disease", superscript_style)
```


```{r, fig.width = 7.5, fig.height = 3.5}
ftext(glue("Table {table_num}: Top five most common physical LTCs in, {HSCP} HSCP as a percentage of the population for {latest_year_ltc}, compared to Scotland."), table_heading_style)

top5_ltc_table

table_num <- table_num + 1
```

Source: Source Linkage Files

## Cancer

For the period `r latest_period_cancer_reg`, there were **`r format_number_for_text(cancer_reg_total_latest)`** new cancer registrations per year on average (a rate of **`r format_number_for_text(cancer_reg_rate_latest)`** registrations per 100,000 age-sex standardised population) in `r HSCP` HSCP. For the period `r latest_period_early_deaths_cancer`, there were also **`r format_number_for_text(early_deaths_cancer_rate_latest)`** early deaths per 100,000 from cancer in the HSCP, this is a **`r format_number_for_text(cancer_deaths_perc_change)`%** `r cancer_deaths_changeword` compared to the rate 10 years prior.

```{r, fig.width = 8.5, fig.height = 3.7, fig.cap = "A line graph showing 10-year time trends for cancer registrations per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": Cancer registration rate over time and by area."), table_heading_style)

cancer_reg_time_trend

figure_num <- figure_num + 1
```

```{r, fig.width = 8.5, fig.height = 3.7, fig.cap = "A line graph showing 10-year time trends for early deaths from cancer per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": Early deaths from cancer (<75 years) over time and by area."), table_heading_style)


early_deaths_cancer_time_trend

figure_num <- figure_num + 1
```

## Hospitalisations by condition

Patient hospitalisations can indicate how certain diseases have varying impacts on people's lives. In the latest time period available in `r HSCP`, the condition with the highest rate of hospitalisations was `r highest_hosp_disease$indicator`.

```{r disease_hosp_table}
ftext(paste0("Table ", table_num, ": Patient hospitalisations by condition and geographical area, age-sex standardised rates per 100,000."), table_heading_style)

flextable(disease_hosp_table, theme_fun = NULL) |>
  lp_flextable_theme() |>
  width(width = 6.5 / ncol(disease_hosp_table)) |>
  set_table_properties(layout = "autofit", width = 1)

table_num <- table_num + 1
```

## Anxiety, Depression and Psychosis (ADP) prescriptions

In `r latest_period_adp_presc`, **`r format_number_for_text(adp_presc_latest)`%** of people were prescribed medication for anxiety, depression or psychosis in `r HSCP` HSCP. This is a **`r format_number_for_text(adp_presc_perc_change)`% `r adp_presc_changeword`** from the rate 10 years prior in `r prev_period_adp_presc` which was `r format_number_for_text(adp_presc_earliest)`%.

```{r, fig.width = 8.5, fig.height = 3.8, fig.cap = "A line graph showing 10-year time trends for anxiety, depression and psychosis prescriptions by percentage of population for Locality, HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": Anxiety, depression and psychosis prescriptions over time and by geographical area."), table_heading_style)

adp_presc_time_trend

figure_num <- figure_num + 1
```

In `r latest_period_adp_presc`, `r HSCP` had a `r adp_presc_diff_scot` proportion of the population being prescribed ADP medication compared to the rest of Scotland (`r format_number_for_text(adp_presc_latest)`% compared to `r format_number_for_text(scot_adp_presc)`%).

```{r, fig.width = 7.5, fig.height = 4.8, fig.cap = "A bar graph showing the percentage of the population prescribed anxiety, depression and psychosis medication in the most recent financial year for all Localities in the partnership and the total percentage for the HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": Percentage population prescribed medication for anxiety, depression and psychosis by area for the latest period available."), table_heading_style)

adp_presc_bar

figure_num <- figure_num + 1
```
