
\newpage

# Housing

\newline

**Summary**

For the most recent time period available, `r LOCALITY` Locality had:

-   **`r n_houses`** dwellings, of which: **`r perc_occupied`%** were occupied and **`r perc_second_homes`%** were second homes.
-   **`r perc_single_discount`%** of dwellers received a single-occupant council tax discount, and **`r perc_exempt`%** were exempt from council tax entirely.
-   **`r perc_houses_AC`%** of houses were within council tax bands A to C, and **`r perc_houses_FH`%** were in bands F to H.

\newline

The graph below shows the number of dwellings in `r LOCALITY` from `r min(house_dat$year)` to `r max_year_housing`.

<!-- <Div custom-style = "Table or chart caption">Figure `r x`: Number of dwellings time trend.</Div> -->

`r ftext(paste0("Figure ",x,": Number of dwellings time trend."),table_heading_style)`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE}
houses_ts

x <- x + 1
```

Of the total number of dwellings in `r max_year_housing`, `r perc_single_discount`% (`r n_single_discount` households) were occupied by an individual receiving a single-occupant council tax discount. Furthermore, `r perc_exempt`% (`r n_exempt` households) were occupied and exempt from council tax.

There were `r n_second_homes` dwellings classed as a second home in `r max_year_housing`, these dwellings made up `r perc_second_homes`% of the households in `r LOCALITY`.


<!-- <Div custom-style = "Table or chart caption">Table `r y`: Breakdown of dwelling types by year for `r LOCALITY` locality.</Div> -->

`r ftext(paste0("Table ",y,": Breakdown of dwelling types by year for ",LOCALITY," locality."),table_heading_style)`


```{r }
flextable(house_table, theme_fun = NULL) %>%
my_ft_format() %>%
  set_header_labels(values = c(
    "Year", "Total Dwellings", "Occupied Dwellings",
    "Vacant Dwellings", "Single Occupant Tax Discount", "Council Tax Exempt Dwellings", "Second Homes"
  ))

y <- y + 1
```

Source: Scottish Assessors' Association (via NRS) \newline

The proportion of households within each council tax band are displayed in the chart below, figures are shown in Table `r y`.


<!-- <Div custom-style = "Table or chart caption">Figure `r x`: Breakdown of households by council tax band for `r LOCALITY` in `r max_year_housing`.</Div> -->

`r ftext(paste0("Figure ",x,": Breakdown of households by council tax band for ",LOCALITY," in ",max_year_housing,"."),table_heading_style)`

```{r fig.width = 7, fig.height = 2, warning = FALSE, fig.cap = 'A bar graph showing the proportion of Households in each council tax band for the locality for the most recent year'}
ctb_plot

x <- x + 1
```


<!-- <Div custom-style = "Table or chart caption">Table `r y`: Percentage of households by council tax band for `r LOCALITY` in `r max_year_housing`.</Div> -->

`r ftext(paste0("Table ",y,": Percentage of households by council tax band for ",LOCALITY," in ",max_year_housing,"."),table_heading_style)`


```{r }
flextable(ctb_table, theme_fun = NULL) %>%
my_ft_format() %>%
  set_header_labels(values = c(
    "Tax Band", "A", "B", "C",
    "D", "E", "F", "G", "H"
  ))

y <- y + 1
```

Source: Scottish Assessors' Association (via NRS)
