\newpage

# Hospital and Community Care

## Summary

**For the most recent time periods available, `r LOCALITY` had:**

-   **`r format(emergency_adm_outputs$current_locality_rate_area,big.mark=",")`** emergency hospital admissions per 100,000 population, compared to `r format(emergency_adm_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

-   **`r format(bed_days_outputs$current_locality_rate_area,big.mark=",")`** unscheduled acute specialty bed days per 100,000 population, compared to `r format(bed_days_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

-   **`r format(ae_attendances_outputs$current_locality_rate_area,big.mark=",")`** A&E attendances per 100,000 population, compared to `r format(ae_attendances_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

-   **`r format(delayed_discharges_outputs$current_locality_rate_area,big.mark=",")`** delayed discharge bed days per 100,000 population aged over 65, compared to `r format(delayed_discharges_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

-   **`r format(falls_outputs$current_locality_rate_area,big.mark=",")`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r format(falls_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

-   **`r format(readmissions_outputs$current_locality_rate_area,big.mark=",")`** emergency readmissions (28 day) per 1,000 discharges, compared to `r format(readmissions_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

-   **`r format(ppa_outputs$current_locality_rate_area,big.mark=",")`** potentially preventable hospital admissions per 100,000 population, compared to `r format(ppa_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

\newpage

## Emergency Admissions

Figure `r figure_num` `r emergency_adm_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r emergency_adm_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": Emergency admissions by geographical area"), table_heading_style)

emergency_adm_outputs$area_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` `r emergency_adm_outputs$intro_paragraph_age`

As presented in Figure `r figure_num`, `r emergency_adm_outputs$age_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE,  fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
ftext(paste0("Figure ", figure_num, ": Emergency admissions by age group"), table_heading_style)

emergency_adm_outputs$age_ts

figure_num <- figure_num + 1
```

\newpage

## Unscheduled Acute Bed Days

Figure `r figure_num` `r bed_days_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r bed_days_outputs$area_text`


```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for unscheduled acute bed days per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": Unscheduled acute bed days by geographical area"), table_heading_style)

bed_days_outputs$area_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` `r bed_days_outputs$intro_paragraph_age`

As presented in Figure `r figure_num`, `r bed_days_outputs$age_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
ftext(paste0("Figure ", figure_num, ": Unscheduled acute bed days by age group"), table_heading_style)

bed_days_outputs$age_ts

figure_num <- figure_num + 1
```

## A&E Attendances

Figure `r figure_num` `r ae_attendances_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r ae_attendances_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population for Locality, HSCP, Health Board and all Scotland."}
ftext(paste0("Figure ", figure_num, ": A&E attendances by geographical area"), table_heading_style)

ae_attendances_outputs$area_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` `r ae_attendances_outputs$intro_paragraph_age`

As presented in Figure `r figure_num`, `r ae_attendances_outputs$age_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population split by age group."}
ftext(paste0("Figure ", figure_num, ": A&E attendances by age group"), table_heading_style)

ae_attendances_outputs$age_ts

figure_num <- figure_num + 1
```

## Emergency Readmissions (28 days)

Figure `r figure_num` `r readmissions_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r readmissions_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Emergency readmissions (28 days) by geographical area"), table_heading_style)

readmissions_outputs$area_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` `r readmissions_outputs$intro_paragraph_age`

As presented in Figure `r figure_num`, `r readmissions_outputs$age_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by age group."}
ftext(paste0("Figure ", figure_num, ": Emergency readmissions (28 days) by age group"), table_heading_style)

readmissions_outputs$age_ts

figure_num <- figure_num + 1
```

\newpage

## Delayed Discharge Bed Days

Figure `r figure_num` `r delayed_discharges_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r delayed_discharges_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for delayed discharge beddays per 100,000 population aged 65+ split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Delayed discharge bed days in the population aged 65+ by geographical area"), table_heading_style)

delayed_discharges_outputs$area_ts

figure_num <- figure_num + 1
```

\newpage

## Emergency admissions from a fall

Figure `r figure_num` `r falls_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r falls_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency admissions from a fall per 100,000 population aged 65+ split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Falls in the population aged 65+ by geographical area"), table_heading_style)

falls_outputs$area_ts

figure_num <- figure_num + 1
```

\newpage

## Potentially Preventable Admissions (PPAs)

Information on the conditions included in Potentially Preventable Admissions (PPA)s is available in Appendix 3. In `r ppa_outputs$max_fin_year`, **`r ppa_outputs$over_65_perc`%** of PPAs in `r LOCALITY` were amongst those aged 65 and over, and **`r ppa_outputs$under_65_perc`%** were amongst those aged under 65.

Figure `r figure_num` presents the PPA rate per 100,000 population in the `r LOCALITY` locality from `r ppa_outputs$min_fin_yea` to `r ppa_outputs$max_fin_yea`. `r ppa_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for potentially preventable admissions per 100,000 population split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Potentially Preventable Admissions (PPAs) by geographical area"), table_heading_style)

ppa_outputs$area_ts

figure_num <- figure_num + 1
```

\newpage

# Hospital Care (Mental Health Specialty)

## Summary

This section looks at mental health-related unscheduled care indicators. For the most recent time period available, `r LOCALITY` had:

-   **`r format(psych_hosp_outputs$current_locality_rate_area,big.mark=",")`** psychiatric patient hospitalisations per 100,000, compared to `r format(psych_hosp_outputs$current_scotland_rate_area,big.mark=",")` in Scotland^4^.
-   **`r format(bed_days_mh_outputs$current_locality_rate_area,big.mark=",")`** unscheduled mental health specialty bed days per 100,000, compared to `r format(bed_days_mh_outputs$current_scotland_rate_area,big.mark=",")` in Scotland.

## Psychiatric patient hospitalisations

Figure `r figure_num` `r psych_hosp_outputs$intro_paragraph`

As presented in Figure `r figure_num`, `r psych_hosp_outputs$indicator_paragraph`

```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing ten-year time trends grouped into 3 year aggregates for psychiatric patient hospitalisations per 100,000 population split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Psychiatric patient hospitalisations by geographical area"), table_heading_style)

psych_hosp_outputs$indicator_ts

figure_num <- figure_num + 1
```

\newpage

## Unscheduled Mental Health Specialty Bed Days

Figure `r figure_num` `r bed_days_mh_outputs$intro_paragraph_area`

As presented in Figure `r figure_num`, `r bed_days_mh_outputs$area_text`

```{r fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Unscheduled mental health specialty bed days by geographical area"), table_heading_style)

bed_days_mh_outputs$area_ts

figure_num <- figure_num + 1
```

Figure `r figure_num` `r bed_days_mh_outputs$intro_paragraph_age`

As presented in Figure `r figure_num`, `r bed_days_mh_outputs$age_text`

```{r fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing six-year time trends for unscheduled mental health specialty bed days per 100,000 population split by geographical area."}
ftext(paste0("Figure ", figure_num, ": Unscheduled mental health specialty bed days by age group"), table_heading_style)

bed_days_mh_outputs$age_ts

figure_num <- figure_num + 1
```
