---
title: ''
output:
  word_document:
    fig_caption: false
    reference_docx: "/conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx"
  html_document:
    fig_caption: false
    df_print: paged
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, warning = FALSE, message = FALSE)
options(kableExtra.auto_format = FALSE)

# Figure and table number objects
x <- 1 # figures
y <- 1 # tables
```

##### Page break

## Notes for this profile

\newline

-   All years shown are calendar years unless otherwise specified.

-   Upper and lower 95% confidence intervals are shown throughout this document where available. In charts, these are displayed as shaded areas on either side of trend lines or as black error bars in bar charts. Confidence intervals show the range of possible values and a certainty that the true value falls within them.

-   Definitions for the indicators shown are available in Appendix 1.

-   Any zero figures for some indicators will indicate either suppression of small data or a complete lack of data available for this locality

##### Page break

## Demographics

\newline

**Summary**

For the most recent time period available, `r HSCP` HSCP had:

-   A total population of **`r total_population`** people, where **`r gender_breakdown[gender_breakdown$sex == "M",]$perc`** were male, and **`r over65`%** were aged over 65.
-   **`r perc_top_quintile`%** of people lived in the least deprived SIMD quintile, and **`r perc_bottom_quintile`%** lived in the most deprived quintile.

\newline

### Population

<!-- Total Population Text -->

In `r pop_max_year`, the total population of `r HSCP` HSCP was `r total_population`. The graph below shows the population distribution of the HSCP. Overall, **`r gender_breakdown[gender_breakdown$sex == "M",]$perc`** of the population are male, and **`r gender_breakdown[gender_breakdown$sex == "F",]$perc`** are female. *Please see the footnotes for more information on NRS population estimates^1^.*

#### Figure `r x`: Population by age and sex.

\newline

```{r echo = FALSE, fig.width = 7, fig.height = 4, warning = FALSE, fig.cap = "A bar chart showing the population distribution of the locality grouped by age and sex"}
pop_pyramid

x <- x + 1
```

<!-- Population over time -->

Figure `r x` shows the historical population of `r HSCP`, along with the NRS population projections. `r pop_graph_text` `r pop_proj_text`. *Please see the footnotes for more information on how the population projections were calculated^2^.*

##### Page break

#### Figure `r x`: Population time trend and projection.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4, warning = FALSE, fig.cap= "A line graph showing the trend in population over time"}
pop_ts_plot

x <- x + 1
```

\newline

Figure `r x` shows how the population structure has changed between `r pop_min_year` and `r pop_max_year`.

#### Figure `r x`: Change in population structure over the last five years.

\newline

```{r echo = FALSE, fig.width = 9, fig.height = 4, warning = FALSE, fig.cap= "A bar chart showing the percentage change in population structure, split by age and sex, over the last five years"}
hist_pop_change

x <- x + 1
```

##### Page break

### Deprivation

The following section explores the deprivation structure of `r HSCP` through the Scottish Index of Multiple Deprivation (SIMD). The SIMD ranks all datazones in Scotland by a number of factors; Access, Crime, Education, Employment, Health, Housing and Income. Based on these ranks, each datazone is then given an overall deprivation rank, which is used to split datazones into Deprivation Quintiles (Quintile 1 being the most deprived, and Quintile 5 the least). The most recent SIMD ranking was carried out in 2020. This section mainly focuses on the SIMD 2020 classifications, however, the 2016 classifications are used to assess how deprivation has changed in `r HSCP` when compared to the rest of Scotland.

Of the `r pop_max_year` population in `r HSCP`, **`r perc_bottom_quintile`%** live in the most deprived Quintile (SIMD 1), and **`r perc_top_quintile`%** live in the least deprived Quintile (SIMD 5).

#### Figure `r x`: Map of Data Zones within `r HSCP` coloured by SIMD quintiles.

```{r echo = FALSE, fig.width = 8, warning = FALSE, fig.cap = 'A map of the locality which is broken down by data zones with the colouring showing the SIMD quintile for each.'}
simd_map

x <- x + 1
```

##### Page break

Table `r y` details the percentage of the HSCP's 2016 population living in the 2016 SIMD Quintiles, the percentage of the `r pop_max_year` population living in the 2020 SIMD Quintiles, and their difference for comparison. Figure `r x` then breaks down SIMD by domain in `r HSCP`.

#### Table `r y`: Percentage of the `r HSCP` population living in the 2016 and 2020 SIMD Datazone Quintiles in 2016 and `r pop_max_year` respectively.

\newline

```{r echo = FALSE}
knitr::kable(simd_diff_overall,
  col.names = c(
    "**Quintile**", "**Percent of 2016 Population (SIMD 2016 Ranking)**",
    glue("**Percent of {pop_max_year} Population (SIMD 2020 Ranking)**"),
    "**Difference**"
  ),
  align = c("l", "r", "r", "r"),
  format = "markdown"
)

y <- y + 1
```

Source: Scottish Government, Public Health Scotland, National Records Scotland. \newline

#### Figure `r x`: Proportion of the population that reside in each 2020 SIMD quintile by domain in `r pop_max_year`.

\newline

```{r echo = FALSE, fig.width = 8, fig.height = 5, warning = FALSE, fig.cap = 'A bar graph showing the proportion of the population in each SIMD decile for each SIMD domain.'}
simd_domains

x <- x + 1
```

##### Page Break

Figure `r x` presents a comparison between the 2016 SIMD ranking applied to 2016 population estimates, and the more recent 2020 SIMD ranking applied to `r pop_max_year` population estimates. The percentages of the population living within each SIMD quintile by domain were calculated using the 2016 and 2020 SIMD datazone classifications respectively. The differences in these percentages are plotted in Figure `r x`. Negative values on the y-axis indicate a decrease in the percent of the population living within a quintile, while positive values indicate an increase in the percent of the population living within a quintile. **Please note that quintiles have been weighted by the Scottish population so, any local changes in SIMD quintile do not necessarily indicate a difference in deprivation, but rather a difference in deprivation in comparison to the rest of Scotland.**

\newline

#### Figure `r x`: Percentage of population in 2016 and `r pop_max_year` living in the 2016 and the 2020 SIMD quintiles by domain.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 7, warning = FALSE, fig.cap = 'Bar graphs showing the percentage change of the population in each SIMD quintile by SIMD domain'}
simd_diff_plot

x <- x + 1
```

##### Page break

## Services

#### Figure `r x`: Map of services by locality in `r HSCP` HSCP^3^.

\newline

```{r echo = FALSE, fig.width=6, fig.cap= "A map of the health and social care partnership including a breakdown on localities with the locations of all the GP practices, care homes, emergency depertments and minor injury units."}
service_map

x <- x + 1
```

\newline

#### Table `r y`: Number of each type of service in `r HSCP` HSCP^3^.

\newline

```{r echo = FALSE}
knitr::kable(services_tibble, col.names = c("**Service Type**", "**Service**", "**Number**"), format = "markdown")

y <- y + 1
```

##### Page break

## Housing

\newline

**Summary**

For the most recent time period available, `r HSCP` HSCP had:

-   **`r n_houses`** dwellings, of which: **`r perc_occupied`%** were occupied and **`r perc_second_homes`%** were second homes.
-   **`r perc_single_discount`%** of dwellers received a single-occupant council tax discount, and **`r perc_exempt`%** were exempt from council tax entirely.
-   **`r perc_houses_AC`%** of houses were within council tax bands A to C, and **`r perc_houses_FH`%** were in bands F to H.

\newline

The graph below shows the number of dwellings in `r HSCP` from `r min(house_dat$year)` to `r max_year_housing`.

#### Figure `r x`: Number of dwellings time trend.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE}
houses_ts

x <- x + 1
```

Of the total number of dwellings in `r max_year_housing`, `r perc_single_discount`% (`r n_single_discount` households) were occupied by an individual receiving a single-occupant council tax discount. Furthermore, `r perc_exempt`% (`r n_exempt` households) were occupied and exempt from council tax.

There were `r n_second_homes` dwellings classed as a second home in `r max_year_housing`, these dwellings made up `r perc_second_homes`% of the households in `r HSCP`.

##### Page break

#### Table `r y`: Breakdown of dwelling types by year for `r HSCP` HSCP.

\newline

```{r echo = FALSE}
knitr::kable(house_table,
  col.names = c(
    "**Year**", "**Total Dwellings**", "**Occupied Dwellings**",
    "**Vacant Dwellings**", "**Single Occupant Tax Discount**", "**Council Tax Exempt Dwellings**", "**Second Homes**"
  ),
  align = c("l", "r", "r", "r", "r", "r", "r"), format = "markdown"
)

y <- y + 1
```

Source: Scottish Assessors' Association (via NRS) \newline

The proportion of households within each council tax band are displayed in the chart below, figures are shown in Table `r y`.

#### Figure `r x`: Breakdown of households by council tax band for `r HSCP` in `r max_year_housing`.

\newline

```{r echo = FALSE, fig.width = 7, fig.height = 2, warning = FALSE, fig.cap = 'A bar graph showing the proportion of Households in each council tax band for the locality for the most recent year'}
ctb_plot

x <- x + 1
```

#### Table `r y`: Percentage of households by council tax band for `r HSCP` in `r max_year_housing`.

\newline

```{r echo = FALSE}
knitr::kable(ctb_table,
  col.names = c(
    "**Tax Band**", "**A**", "**B**", "**C**",
    "**D**", "**E**", "**F**", "**G**", "**H**"
  ),
  align = c("l", rep("r", 8)), format = "markdown"
)

y <- y + 1
```

Source: Scottish Assessors' Association (via NRS)

##### Page break

## General Health

### Summary

\newline

For the most recent time period available^4^, `r HSCP` HSCP had:

```{r life_exp_text, echo = FALSE}
if (is.na(avg_life_exp_latest_male)) {
  life_exp_text <- "No data available for life expectancy."
  life_exp_text2 <- "No data available for life expectancy at locality level."
} else {
  life_exp_text <- glue("An average life expectancy of **{avg_life_exp_latest_male}** years for males and **{avg_life_exp_latest_fem}** years for females, compared to the national average of {scot_life_exp_male} and {scot_life_exp_fem} years of age respectively.")
  life_exp_text2 <- glue("In the latest time period available from {latest_period_life_exp_otherareas} (3-year aggregate), the average life expectancy in {HSCP} HSCP was {avg_life_exp_latest_male} years for men, and {avg_life_exp_latest_fem} years for women. A 10-year time trend can be seen in figure {x}.")
}
```

-   `r life_exp_text`
-   A death rate for ages 15 to 44 of **`r format_number_for_text(deaths_15_44_latest)`** deaths per 100,000 age-sex standardised population. This is `r deaths_15_44_diff_scot` than Scotland (`r format_number_for_text(scot_deaths_15_44)` deaths per 100,000)^4^.
-   **`r format_number_for_text(ltc_percent_total_latest)`%** of the HSCP's population with at least one long-term physical health condition. This is `r ltc_diff_scot` than Scotland (`r format_number_for_text(ltc_perc_scot)`%).
-   A cancer registration rate of **`r format_number_for_text(cancer_reg_rate_latest)`** registrations per 100,000 age-sex standardised population (compared to `r format_number_for_text(scot_cancer)` in Scotland), and an early death rate (\<75 years) from cancer of **`r format_number_for_text(early_deaths_cancer_rate_latest)`** per 100,000 age-sex standardised population (compared to `r format_number_for_text(scot_cancer_deaths)` in Scotland)^4^.
-   **`r format_number_for_text(adp_presc_latest)`%** of the population being prescribed medication for anxiety, depression, or psychosis. This is a `r adp_presc_diff_scot` proportion than Scotland (`r format_number_for_text(scot_adp_presc)`%).

\newline

### Life Expectancy

`r life_exp_text2`

#### Figure `r x`: Average life expectancy in men and women over time. \newline

```{r life_exp_trend, echo = FALSE, fig.width = 8, fig.height = 4.5, fig.cap = 'A line graph showing the trent for average life expectancy in the locality for male and female residents'}
if (HSCP %in% check_missing_data_scotpho(life_exp)$area_name) {
  print("No data available for this locality")
} else {
  life_exp_trend
}

x <- x + 1
```

##### Page break

Table `r y` provides the average life expectancy for men and women in different areas for the latest time period available.

#### Table `r y`: Average life expectancy in years for the latest time periods (`r latest_period_life_exp_loc` aggregated years for the HSCP; `r latest_period_life_exp_otherareas` aggregated years for other areas).

\newline

```{r life_exp_table, echo = FALSE}
knitr::kable(life_exp_table)

y <- y + 1
```

Source: ScotPHO

\newline

`r if(HSCP == "Clackmannanshire and Stirling") {"Note that data is unavailable for Clackmannanshire & Stirling HSCP."}`

\newline

### Deaths, aged 15 to 44

The following chart shows a trend of death rates among people aged 15 to 44 per 100,000 age-sex standardised population^4^ by area. In the most recent aggregate time period available (`r latest_period_deaths_15_44`), the mortality rate in `r HSCP` HSCP was **`r format_number_for_text(deaths_15_44_latest)`** deaths per 100,000 population.

#### Figure `r x`: Deaths aged 15 to 44 years by geographical area and over time. \newline

```{r deaths_15_44_time_trend, echo = FALSE, fig.width = 8.5, fig.height = 4.2, fig.cap = 'A line graph showing the ten-year time trend for the 3-year aggregate rate of deaths per 100,000 population for 15 to 44 year olds by HSCP, health board and all Scotland'}
deaths_15_44_time_trend

x <- x + 1
```

##### Page break

Figure `r x` provides comparisons of deaths at ages 15 to 44 across all areas including other localities in `r HSCP` HSCP. In `r latest_period_deaths_15_44`, `r HSCP` had a `r deaths_15_44_diff_scot` rate than the rest of Scotland (`r format_number_for_text(deaths_15_44_latest)` compared to `r format_number_for_text(scot_deaths_15_44)` deaths per 100,000).

#### Figure `r x`: Deaths at ages 15 to 44 by area for the latest time period available. \newline

```{r deaths_15_44_bar, echo = FALSE, fig.width = 7.5, fig.height = 4.8, fig.cap = 'A bar graph showing the rate of deaths per 100,000 population for residents aged 15 to 44 by HSCP, health board and all Scotland and for other localitiies in the HSCP between 2019 and 2021.'}
deaths_15_44_bar

x <- x + 1
```

##### Page break

### Long-Term Physical Health Conditions and Multi-morbidity

\newline

In the financial year `r latest_year_ltc`, in `r HSCP` HSCP, it is estimated that **`r format_number_for_text(ltc_percent_total_latest)`%** of the population had at least one physical long-term condition (LTC). These include cardiovascular, neurodegenerative, and respiratory conditions, as well as other organ conditions (namely liver disease and renal failure), arthritis, cancer, diabetes, and epilepsy. *Please note that estimates for this section are based on people who had contact with NHS services - see footnotes for further information and caveats on identifying LTCs.^6^*

```{r ltc_waffles, echo = FALSE, fig.width = 9, fig.height = 3.5, fig.cap = 'Infographic split by age group showing the number of people out of ten that have at least one LTC. The age groups shown are under 65, 65-74, 75-84, and over 85.'}
ltc_waffles
```

\newline

The co-occurrence of two or more conditions, known as multi-morbidity, is broken down in Table `r y`, distinguishing between age groups. Overall, **`r format_number_for_text(ltc_multimorbidity_un65_perc)`**% of those under 65 have more than one LTC, compared to **`r format_number_for_text(ltc_multimorbidity_ov65_perc)`**% of those over 65.

#### Table `r y`: Multi-morbidity of physical long-term conditions by age group in `r latest_year_ltc`. \newline

```{r ltc_multimorbidity_table, echo = FALSE}
knitr::kable(ltc_multimorbidity_table)

y <- y + 1
```

##### Page break

**Most common physical Long-Term Conditions (LTCs)**

Below is a breakdown of the physical LTCs, for the financial year `r latest_year_ltc`. Figure `r x` shows the prevalence of different LTCs in each age group in `r HSCP` HSCP, and Table `r y` illustrates the five most prevalent physical LTCs across all ages at the partnership, and Scotland levels.

#### Figure `r x`: The percentage of people with each physical LTC by age group. \newline

```{r ltc_types_plot, echo = FALSE, fig.width = 7.5, fig.height = 5, fig.cap = "A graph showing the prevalence of physical long term conditions by percentage of population for Under 65s and for Over 65s."}
ltc_types_plot

x <- x + 1
```

\*COPD: Chronic Obstructive Pulmonary Disease

#### Table `r y`: Prevalence of the five most common physical LTCs as a percentage of the population across geographical areas (1 is the most prevalent).

\newline

```{r top5_ltc_table, echo = FALSE, fig.width = 7.5, fig.height = 3.5}
top5_ltc_table

y <- y + 1
```

Source: Source Linkage Files

### Cancer

For the period `r latest_period_cancer_reg`, there were **`r format_number_for_text(cancer_reg_total_latest)`** new cancer registrations per year on average (a rate of **`r format_number_for_text(cancer_reg_rate_latest)`** registrations per 100,000 age-sex standardised population) in `r HSCP` HSCP. For the period `r latest_period_early_deaths_cancer`, there were also **`r format_number_for_text(early_deaths_cancer_rate_latest)`** early deaths per 100,000 from cancer in the HSCP, this is a **`r format_number_for_text(cancer_deaths_perc_change)`%** `r cancer_deaths_changeword` compared to the rate 10 years prior.

#### Figure `r x`: Cancer registration rate over time and by area. \newline

```{r cancer_reg_time_trend, echo = FALSE, fig.width = 8.5, fig.height = 3.7, fig.cap = "A line graph showing 10-year time trends for cancer registrations per 100,000 population for HSCP, Health Board and all Scotland."}
cancer_reg_time_trend

x <- x + 1
```

#### Figure `r x`: Early deaths from cancer (\<75 years) over time and by area. \newline

```{r early_deaths_cancer_time_trend, echo = FALSE, fig.width = 8.5, fig.height = 3.7, fig.cap = "A line graph showing 10-year time trends for early deaths from cancer per 100,000 population for HSCP, Health Board and all Scotland."}
early_deaths_cancer_time_trend

x <- x + 1
```

##### Page break

### Hospitalisations by condition

Patient hospitalisations can indicate how certain diseases have varying impacts on people's lives. In the latest time period available in `r HSCP`, the condition with the highest rate of hospitalisations was `r highest_hosp_disease$indicator`.

#### Table `r y`: Patient hospitalisations by condition and geographical area, age-sex standardised rates per 100,000.

```{r disease_hosp_table, echo = FALSE}
knitr::kable(disease_hosp_table)

y <- y + 1
```

\newline

### Anxiety, Depression and Psychosis (ADP) prescriptions

In `r latest_period_adp_presc`, **`r format_number_for_text(adp_presc_latest)`%** of people were prescribed medication for anxiety, depression or psychosis in `r HSCP` HSCP. This is a **`r format_number_for_text(adp_presc_perc_change)`% `r adp_presc_changeword`** from the rate 10 years prior in `r prev_period_adp_presc` which was `r format_number_for_text(adp_presc_earliest)`%.

#### Figure `r x`: Anxiety, depression and psychosis prescriptions over time and by geographical area. \newline

```{r adp_presc_time_trend, echo = FALSE, fig.width = 8.5, fig.height = 3.8, fig.cap = "A line graph showing 10-year time trends for anxiety, depression and psychosis prescriptions by percentage of population for HSCP, Health Board and all Scotland."}
adp_presc_time_trend

x <- x + 1
```

##### Page break

In `r latest_period_adp_presc`, `r HSCP` had a `r adp_presc_diff_scot` proportion of the population being prescribed ADP medication compared to the rest of Scotland (`r format_number_for_text(adp_presc_latest)`% compared to `r format_number_for_text(scot_adp_presc)`%).

#### Figure `r x`: Percentage population prescribed medication for anxiety, depression and psychosis by area for the latest period available. \newline

```{r adp_presc_bar, echo = FALSE, fig.width = 7.5, fig.height = 4.8, fig.cap = "A bar graph showing the percentage of the population prescribed anxiety, depression and psychosis medication in the most recent financial year for all Localities in the partnership and the total percentage for the HSCP, Health Board and all Scotland."}
adp_presc_bar

x <- x + 1
```

##### Page break

## Lifestyle and Risk Factors

\newline

**Summary**

Mental and physical well-being has close ties with people's lifestyles and behaviours. Financial security, employment and location are influences that often have a bearing on these choices. Issues can develop when alcohol, smoking or drug use shape lives. This section provides data on drug-related hospital admissions, alcohol-related hospital admissions, alcohol-specific deaths and bowel screening uptake, to give an overview of some of the lifestyles and behaviours for the `r HSCP` HSCP. These can give an idea of quality of life and prosperity.

For the most recent time period available^4^, `r HSCP` had:

-   **`r format_number_for_text(alcohol_hosp_latest)`** alcohol-related hospital admissions per 100,000 age-sex standardised population. This is `r alcohol_hosp_diff_scot` than Scotland (`r  format_number_for_text(scot_alcohol_hosp)` admissions per 100,000)^5^.
-   **`r format_number_for_text(alcohol_deaths_latest)`** alcohol-specific deaths per 100,000 age-sex standardised population. This is `r alcohol_deaths_diff_scot` than Scotland (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000)^5^.
-   **`r format_number_for_text(drug_hosp_latest)`** drug-related hospital admissions per 100,000 age-sex standardised population. This is `r drug_hosp_diff_scot` than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000)^5^.
-   **`r format_number_for_text(bowel_screening_latest)`%** uptake of bowel screening among the eligible population, compared to `r format_number_for_text(scot_bowel_screening)`% in Scotland.

\newline

### Alcohol-related Hospital Admissions

In `r latest_period_alcohol_hosp`, the rate of alcohol-related admissions was **`r format_number_for_text(alcohol_hosp_latest)`** per 100,000 age-sex standardised population in `r HSCP`. This is `r get_article(alcohol_hosp_change)` `r format_number_for_text(alcohol_hosp_change)`% `r alcohol_hosp_change_word` overall since `r earliest_period_alcohol_hosp`. Figure `r x` shows a trend of alcohol-related hospital admissions for `r HSCP` HSCP compared with `r HB`, and Scotland from financial year `r earliest_period_alcohol_hosp` to `r latest_period_alcohol_hosp`.

Figure `r x + 1` then compares different areas, including the other localities in `r HSCP`, for the latest financial year. This bar chart shows that in `r latest_period_alcohol_hosp`, `r HSCP` HSCP had a `r alcohol_hosp_diff_scot` alcohol-related hospital admissions rate compared to Scotland (`r format_number_for_text(alcohol_hosp_latest)` and `r  format_number_for_text(scot_alcohol_hosp)` admissions respectively).

##### Page break

#### Figure `r x`: Alcohol-related hospital admission rates by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing 10-year time trends for alcohol-related hospital admissions per 100,000 population for HSCP, Health Board and all Scotland."}
alcohol_hosp_time_trend

x <- x + 1
```

#### Figure `r x`: Alcohol-related hospital admissions by area for the latest time period.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE, fig.cap = "A bar graph showing alcohol-related hospital admissions per 100,000 population for  HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent financial year."}
alcohol_hosp_bar

x <- x + 1
```

\newline

### Alcohol-Specific Deaths

Data on alcohol-specific deaths is available as 5-year aggregates. In `r HSCP`, the latest rate of alcohol-specific deaths was **`r format_number_for_text(alcohol_deaths_latest)`** deaths per 100,000 age-sex standardised population. This is `r format_number_for_text(alcohol_deaths_change)`% `r alcohol_deaths_change_word` than the rate in `r earliest_period_alcohol_deaths`. Figure `r x + 1` also shows that the HSCP has a `r alcohol_deaths_diff_scot` alcohol-specific death rate compared to Scotland overall (`r  format_number_for_text(scot_alcohol_deaths)` deaths per 100,000).

#### Figure `r x`: Alcohol-specific deaths by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing 10-year time trends for 5 year aggregate rates of alcohol-specific deaths per 100,000 population for HSCP, Health Board and all Scotland."}
alcohol_deaths_time_trend

x <- x + 1
```

#### Figure `r x`: Alcohol-specific deaths by area for the latest time period available.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.5, warning = FALSE, fig.cap =  "A bar graph showing the 5 year aggregate rate of alcohol-specific deaths per 100,000 population for HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent time period."}
alcohol_deaths_bar

x <- x + 1
```

\newline

### Drug-related Hospital Admissions

There were **`r format_number_for_text(drug_hosp_latest)`** drug-related hospital admissions per 100,000 age-sex standardised population^4^ in the `r HSCP` HSCP in the time period `r latest_period_drug_hosp` (3-year financial year aggregate). This is `r get_article(drug_hosp_change)` `r format_number_for_text(drug_hosp_change)`% `r drug_hosp_change_word` since `r earliest_period_drug_hosp`. A trend of the change in drug-related hospital admissions for the locality and comparable areas is shown in Figure `r x` from `r earliest_period_drug_hosp_trend` onward.

A comparison of areas at the most recent time period (`r latest_period_drug_hosp` aggregated financial years) is available in Figure `r x + 1` This shows the `r HSCP` HSCP has a `r drug_hosp_diff_scot` rate of drug-related hospital admissions than Scotland (`r format_number_for_text(scot_drug_hosp)` admissions per 100,000).

#### Figure `r x`: Drug-related hospital admission rates by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing time trends for 3 year aggregate rates of drug-related hospital admissions per 100,000 population for HSCP, Health Board and all Scotland."}
drug_hosp_time_trend

x <- x + 1
```

##### Page break

#### Figure `r x`: Drug-related hospital admission rates by area for the latest time period available.

```{r echo = FALSE, fig.width = 8, fig.height = 4.8, warning = FALSE, fig.cap= "A bar graph showing the 3 year rate of drug-related hospital admissions per 100,000 population for HSCP, Health Board and all Scotland and all other localities in the HSCP for the most recent time period."}
drug_hosp_bar

x <- x + 1
```

\newline

### Bowel Screening Uptake

Bowel screening is offered every two years to eligible men and women aged between 50-74 years old. Eligible people are posted a test kit which is completed at home. Since 1st April 2013, those aged 75 and over can also self-refer and opt into screening.

A trend of the percentage uptake of bowel screening among the eligible population is shown for `r HSCP` and comparable areas. Data is presented as 3-year aggregates. The `r latest_period_bowel_screening` uptake rate for `r HSCP` is **`r format_number_for_text(bowel_screening_latest)`%**. This is `r get_article(bowel_screening_change)` `r format_number_for_text(bowel_screening_change)`% `r bowel_screening_change_word` since `r earliest_period_bowel_screening`. As can be seen in Figure `r x + 1`, in the latest estimate, the uptake in `r HSCP` was `r bowel_screening_diff_scot` than the uptake in Scotland overall (`r format_number_for_text(scot_bowel_screening)`%).

##### Page break

#### Figure `r x`: Bowel screening uptake for eligible men and women, by area and over time.

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing time trends for 3 year aggregate rates for bowel screening uptake by percentage of eligible population for HSCP, Health Board and all Scotland."}
bowel_screening_time_trend

x <- x + 1
```

#### Figure `r x`: Bowel screening uptake by area for the latest time period available.

\newline

```{r echo = FALSE, fig.width = 7.5, fig.height = 4.8, warning = FALSE, fig.cap = "A bar graph showing the most recent 3 year aggregate rates for bowel screening uptake by percentage of eligible population for HSCP, Health Board and all Scotland and for all localities within the HSCP."}
bowel_screening_bar

x <- x + 1
```

##### Page break

## Hospital and Community Care

\newline

**Summary**

**For the most recent time periods available, `r HSCP` had:**

-   **`r hscp_emergency_adm1 `** emergency hospital admissions per 100,000 population, compared to `r scot_emergency_adm1` in Scotland.

-   **`r hscp_bed_days1 `** unscheduled acute specialty bed days per 100,000 population, compared to `r scot_bed_days1` in Scotland.

-   **`r hscp_ae_att1`** A&E attendances per 100,000 population, compared to `r scot_ae_att1` in Scotland.

-   **`r hscp_dd1`** delayed discharge bed days per 100,000 population aged over 65, compared to `r scot_dd1` in Scotland.

-   **`r hscp_falls1`** emergency hospital admissions from falls per 100,000 population aged over 65, compared to `r scot_falls1` in Scotland.

-   **`r hscp_read`** emergency readmissions (28 day) per 1,000 discharges, compared to `r scot_read` in Scotland.

-   **`r hscp_ppa$formatted_data[2]`** potentially preventable hospital admissions per 100,000 population, compared to `r scot_ppa$formatted_data[2]` in Scotland.

##### Page break

### Emergency Admissions

Figure `r x` presents the emergency admissions rate per 100,000 population in the `r HSCP` HSCP from `r min_year_ea` to `r max_year_ea`.

As presented in Figure `r x`, the emergency admissions rate in the `r HSCP` HSCP for `r max_year_ea` is `r hscp_emergency_adm1`, `r get_article(hscp_rate_change)` `r hscp_rate_change`% `r word_change_hscp` since `r min_year_ea`. The `r HB` health board rate is `r hb_emergency_adm1` in `r max_year_ea`, `r get_article(hb_rate_change)` `r hb_rate_change`% `r word_change_hb` since `r min_year_ea` and the Scotland rate is `r scot_emergency_adm1`, `r get_article(scot_rate_change)` `r scot_rate_change`% `r word_change_scot` since `r min_year_ea`.

#### Figure `r x`: Emergency admissions by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population for HSCP, Health Board and all Scotland."}
EAs_loc_ts

x <- x + 1
```

Figure `r x` presents the emergency admissions rate per 100,000 population in the `r HSCP` HSCP from `r min_ea_age` to `r max_ea_age` by age group.

As presented in Figure `r x`, the highest emergency admissions rate for the `r HSCP` HSCP in `r max_ea_age` is `r latest_ea_max_age1` per 100,000 population for the `r age_group_max_ea` age group with a percentage `r max_word_change_ea` of `r max_rate_change_ea`% since `r min_ea_age`. The lowest emergency admissions rate for `r HSCP` in `r max_ea_age` is `r latest_ea_min_age1` per 100,000 population for the `r age_group_min_ea` age group with a percentage `r min_word_change_ea` of `r min_rate_change_ea`% since `r min_ea_age`.

#### Figure `r x`: Emergency admissions by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE,  fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
EAs_age_ts

x <- x + 1
```

##### Page break

### Unscheduled Acute Bed Days

Figure `r x` presents the unscheduled bed days rate per 100,000 population in the `r HSCP` HSCP from `r min_year_ubd` to `r max_year_ubd`.

As presented in Figure `r x`, the unscheduled bed days rate in the `r HSCP` HSCP is `r hscp_bed_days1`, `r get_article(hscp_rate_ubd)` `r hscp_rate_ubd`% `r hscp_change_ubd` since `r min_year_ubd`. The `r HB` health board rate for `r max_year_ubd` is `r hb_bed_days1`, `r get_article(hb_rate_change_ubd)` `r hb_rate_change_ubd`% `r word_change_hb_ubd` since `r min_year_ubd` and the Scotland rate is `r scot_bed_days1`, `r get_article(scot_rate_ubd)` `r scot_rate_ubd`% `r scot_change_ubd` since `r min_year_ubd`.

#### Figure `r x`: Unscheduled acute bed days by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for unscheduled acute bed days per 100,000 population for  HSCP, Health Board and all Scotland."}
BDs_loc_ts

x <- x + 1
```

Figure `r x` presents the unscheduled bed days rate per 100,000 population in the `r HSCP` HSCP from `r min_ubd_age` to `r max_ubd_age` by age group.

As presented in Figure `r x`, the highest unscheduled bed days rate for the `r HSCP` HSCP in `r max_ubd_age` is `r latest_ubd_max_age1` bed days per 100,000 population for the `r age_group_max_ubd` age group with a percentage `r max_word_change_ubd` of `r max_rate_change_ubd`% since `r min_ubd_age`. The lowest unscheduled bed days rate for `r HSCP` in `r max_ubd_age` is `r latest_ubd_min_age1` bed days per 100,000 population for the `r age_group_min_ubd` age group with a percentage `r min_word_change_ubd` of `r min_rate_change_ubd`% since `r min_ubd_age`.

#### Figure `r x`: Unscheduled acute bed days by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for emergency admissions per 100,000 population split by age group."}
BDs_age_ts

x <- x + 1
```

##### Page break

### A&E Attendances

Figure `r x` presents the A&E attendance rate per 100,000 population in the `r HSCP` HSCP from `r min_year_ae_area` to `r max_year_ae_area`.

As presented in Figure `r x`, the A&E attendance rate per 100,000 in the `r HSCP` HSCP is `r hscp_ae_att1`, `r get_article(percent_rate_change_ae_areas_hscp)` `r percent_rate_change_ae_areas_hscp`% `r word_change_rate_ae_areas_hscp` since `r min_year_ae_area`. The `r HB` health board rate for `r max_year_ae_area` is `r hb_ae1`, `r get_article(hb_rate_change_ae)` `r hb_rate_change_ae`% `r word_change_hb_ae` since `r min_year_ae_area` and the Scotland rate is `r scot_ae_att1`, `r get_article(percent_rate_change_ae_areas_scot)` `r percent_rate_change_ae_areas_scot`% `r word_change_rate_ae_areas_scot` since `r min_year_ae_area`.

#### Figure `r x`: A&E attendances by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population for HSCP, Health Board and all Scotland."}
AandE_loc_ts

x <- x + 1
```

Figure `r x` presents the A&E attendance rate per 100,000 population in the `r HSCP` HSCP from `r min_year_ae_area` to `r max_year_ae_area` by age group.

As presented in Figure `r x`, the highest A&E attendance rate for the `r HSCP` HSCP in `r max_year_ae_age` is `r latest_ae_att_loc1_age` per 100,000 population for the `r age_group_max` age group with a percentage `r word_change_rate_ae_age` of `r percent_rate_change_ae_age`% since `r min_year_ae_age`. The lowest A&E attendance rate for `r HSCP` in `r max_year_ae_age` is `r latest_ae_att_loc1_age_min` per 100,000 population for the `r age_group_min` age group with a percentage `r word_change_rate_ae_age2` of `r percent_rate_change_ae_age2`% since `r min_year_ae_age`.

#### Figure `r x`: A&E attendances by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for A&E attendancess per 100,000 population split by age group."}
AandE_age_ts

x <- x + 1
```

##### Page break

### Emergency Readmissions (28 days)

Figure `r x` presents the emergency readmission (28 days) rate per 1,000 discharges in the `r HSCP` HSCP from `r min_year_re_area` to `r max_year_re_area`.

As presented in Figure `r x`, the emergency readmission (28 days) rate per 1,000 discharges in the `r HSCP` HSCP is `r hscp_read`, `r get_article(percent_rate_change_re_area_hscp)` `r percent_rate_change_re_area_hscp`% `r word_change_rate_re_area_hscp` since `r min_year_re_area`. The `r HB` health board rate for `r max_year_re_area` is `r hb_read1`, `r get_article(hb_rate_change_read)` `r hb_rate_change_read`% `r word_change_hb_read` since `r min_year_re_area` and the Scotland rate is `r scot_read`, `r get_article(percent_rate_change_re_area_scot)` `r percent_rate_change_re_area_scot`% `r word_change_rate_re_area_scot` since `r min_year_re_area`.

#### Figure `r x`: Emergency readmissions (28 days) by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by geographical area."}
read_loc_ts

x <- x + 1
```

Figure `r x` presents the emergency readmission (28 days) rate per 1,000 discharges in the `r HSCP` HSCP from `r min_year_re_age` to `r max_year_re_age` by age group.

As presented in Figure `r x`, the highest emergency readmission (28 days) rate for the `r HSCP` HSCP in `r max_year_re_age` is `r latest_re_max_age_data` per 1,000 discharges for the `r latest_re_max_age_group` age group with a percentage `r word_change_rate_re_age` of `r percent_rate_change_re_age`% since `r min_year_re_age`. The lowest emergency readmission (28 days) rate for the `r HSCP` HSCP in `r max_year_re_age` is `r latest_re_min_age_data` per 1,000 discharges for the `r latest_re_min_age_group` age group with a percentage `r word_change_rate_re_age_min` of `r percent_rate_change_re_age_min`% since `r min_year_re_age`.

#### Figure `r x`: Emergency readmissions (28 days) by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency readmissions per 1,000 discharges split by age group."}
read_age_ts

x <- x + 1
```

##### Page break

### Delayed Discharge Bed Days

Figure `r x` presents the number of delayed discharge bed days per 100,000 population aged over 65+ in the `r HSCP` HSCP from `r min_year_dd` to `r max_year_dd`.

As presented in Figure `r x`, the number of delayed discharge bed days per 100,000 population aged over 65+ in the `r HSCP` HSCP is `r hscp_dd1`, `r get_article(percent_rate_change_dd_hscp)` `r percent_rate_change_dd_hscp`% `r word_change_rate_dd_hscp` since `r min_year_dd`. The `r HB` health board rate for `r max_year_dd` is `r hb_dd1`, `r get_article(hb_rate_change_dd)` `r hb_rate_change_dd`% `r word_change_hb_dd` since `r min_year_dd` and the Scotland rate is `r scot_dd1`, `r get_article(percent_rate_change_dd_scot)` `r percent_rate_change_dd_scot`% `r  word_change_rate_dd_scot` since `r min_year_dd`.

#### Figure `r x`: Delayed discharge bed days in the population aged 65+ by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for delayed discharge beddays per 100,000 population aged 65+ split by geographical area."}
DD_loc_ts

x <- x + 1
```

### Emergency admissions from a fall

Figure `r x` presents the emergency admissions from falls rate per 100,000 population aged 65 and over in the `r HSCP` HSCP from `r min_year_falls` to `r max_year_falls`.

As presented in Figure `r x`, the emergency admissions from falls rate per 100,000 population aged over 65+ in the `r HSCP` HSCP is `r hscp_falls1`, `r get_article(percent_rate_change_falls_hscp)` `r percent_rate_change_falls_hscp`% `r word_change_rate_falls_hscp` since `r min_year_falls`. The `r HB` health board rate for `r max_year_falls` is `r hb_falls1`, `r get_article(hb_rate_change_falls)` `r hb_rate_change_falls`% `r word_change_hb_falls` since `r min_year_falls` and the Scotland rate is `r scot_falls1`, `r get_article(percent_rate_change_falls_scot)` `r percent_rate_change_falls_scot`% `r  word_change_rate_falls_scot` since `r min_year_falls`.

#### Figure `r x`: Falls in the population aged 65+ by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for emergency admissions from a fall per 100,000 population aged 65+ split by geographical area."}
Falls_loc_ts

x <- x + 1
```

##### Page break

### Potentially Preventable Admissions (PPAs)

Information on the conditions included in Potentially Preventable Admissions (PPA)s is available in Appendix 3. In `r max_fy`, **`r latest_ppa_65plus`%** of PPAs in `r HSCP` were amongst those aged 65 and over, and **`r latest_ppa_under65`%** were amongst those aged under 65.

Figure `r x` presents the PPA rate per 100,000 population in the `r HSCP` HSCP from `r min_year_ppa_areas` to `r max_year_ppa_areas`. The rate per 100,000 population for PPAs in the `r HSCP` HSCP for `r max_year_ppa_areas` is `r hscp_ppa$data[2]`, `r get_article(ppa_diff_hscp)` `r ppa_diff_hscp`% `r ppa_word_change_hscp` since `r hscp_ppa$financial_year[1]`. The `r HB` health board rate for `r hb_ppa$financial_year[2]` is `r hb_ppa$formatted_data[2]`, `r get_article(diff_hb_ppa)` `r diff_hb_ppa`% `r word_change_hb_ppa` since `r hb_ppa$financial_year[]` and the Scotland rate is `r scot_ppa$formatted_data[2]`, `r get_article(diff_scot_ppa)` `r diff_scot_ppa`% `r  word_change_scot_ppa` since `r hb_ppa$financial_year[1]`.

#### Figure `r x`: Potentially Preventable Admissions (PPAs) by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing seven-year time trends for potentially preventable admissions per 100,000 population split by geographical area."}
ppa_loc_ts

x <- x + 1
```

\newline

##### Page break

## Hospital Care (Mental Health Speciality)

\newline

**Summary**

This section looks at mental health-related unscheduled care indicators. For the most recent time period available, `r HSCP` had:

-   **`r psych_hosp_latest`** psychiatric patient hospitalisations per 100,000, compared to `r scot_psych_hosp$measure[2]` in Scotland^5^.
-   **`r hscp_bed_days_mh1`** unscheduled mental health specialty bed days per 100,000, compared to `r scot_bed_days_mh1` in Scotland.

\newline

### Psychiatric patient hospitalisations

Figure `r x` presents the psychiatric patient hospitalisation 3-year aggregate rate per 100,000 population in the `r HSCP` HSCP from `r hscp_psych_hosp$period_short[1]` to `r hscp_psych_hosp$period_short[2]`.

As presented in Figure `r x`, the 3-year aggregate psychiatric patient hospitalisation rate per 100,000 population in the `r HSCP` HSCP for `r loc_psych_hosp$period_short[2]` is `r hscp_psych_hosp$measure[2]`, `r get_article(diff_hscp_psych)` `r diff_hscp_psych`% `r word_change_hscp_psych` since `r hscp_psych_hosp$period_short[1]`. The `r HB` health board the 3-year aggregate rate for `r hb_psych_hosp$period_short[2]` is `r hb_psych_hosp$measure[2]`, `r get_article(diff_hb_psych)` `r diff_hb_psych`% `r word_change_hb_psych` since `r hscp_psych_hosp$period_short[1]` and the Scotland the 3-year aggregate rate is `r scot_psych_hosp$measure[2]`, `r get_article(diff_scot_psych)` `r diff_scot_psych`% `r word_change_scot_psych` since `r hscp_psych_hosp$period_short[1]`.

#### Figure `r x`: Psychiatric patient hospitalisations by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing ten-year time trends grouped into 3 year aggregates for psychiatric patient hospitalisations per 100,000 population split by geographical area."}
psych_hosp_time_trend

x <- x + 1
```

##### Page break

### Unscheduled Mental Health Specialty Bed Days

Figure `r x` presents the unscheduled mental health bed days rate per 100,000 population in the `r HSCP` HSCP from `r min_year_bd_mh_areas` to `r max_year_bd_mh_areas`.

As presented in Figure `r x`, the unscheduled mental health bed days rate per 100,000 population in the `r HSCP` HSCP is `r hscp_bed_days_mh1`, `r get_article(hscp_rate_change_beds_mh)` `r hscp_rate_change_beds_mh`% `r hscp_word_change_beds_mh` since `r min_year_bd_mh_areas`. The `r HB` health board rate for `r max_year_bd_mh_areas` is `r hb_mh_beddays1`, `r get_article(hb_rate_change_mh)` `r hb_rate_change_mh`% `r word_change_hb_mh` since `r  min_year_bd_mh_areas` and the Scotland rate is `r scot_bed_days_mh1`, `r get_article(scot_rate_change_beds_mh)` `r scot_rate_change_beds_mh`% `r  scot_word_change_beds_mh` since `r min_year_bd_mh_areas`.

#### Figure `r x`: Unscheduled mental health specialty bed days by geographical area

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_loc_ts

x <- x + 1
```

Figure `r x` presents the unscheduled mental health bed days rate per 100,000 in the `r HSCP` HSCP from `r min_year_bd_mh_age` to `r max_year_bd_mh_age` by age group.

As presented in Figure `r x`, the highest unscheduled mental health bed days rate for the `r HSCP` HSCP in `r max_year_bd_mh_age` is `r latest_bd_mh_max_age1` per 100,000 population for the `r age_group_max_mh` age group with a percentage `r max_word_change_beds_mh` of `r max_rate_change_beds_mh`% since `r min_year_bd_mh_age`. The lowest unscheduled mental health bed days rate for the `r HSCP` HSCP in `r max_year_bd_mh_age` is `r latest_bd_mh_min_age1` per 100,000 population for the `r age_group_min_mh` age group with a percentage `r min_word_change_beds_mh` of `r min_rate_change_beds_mh`% since `r min_year_bd_mh_age1`.

#### Figure `r x`: Unscheduled mental health specialty bed days by age group

\newline

```{r echo = FALSE, fig.width = 8.5, fig.height = 4.5, warning = FALSE, fig.cap = "A line graph showing six-year time trends for uncscheduled mental health specialty bed days per 100,000 population split by geographical area."}
BDMH_age_ts

x <- x + 1
```

##### Page Break

### Footnotes

1. As of February 2025, the NRS population estimate files are in a transitional phase. The small area population estimates (SAPE) for localities extend only to 2022 and are based on the 2011 data zones. NRS will not rebase estimates for 2011-2021 in these SAPE files. Only the 2022 data zone SAPE will include updated figures for the years 2011-2022, expected to be available in summer 2025. While rebased estimates are available at the HSCP level up to 2023, they have been excluded from locality profiles to ensure consistency between locality and HSCP population estimates and rates.

2. Currently, NRS does not provide population projections at the locality level. To estimate future population changes in `r HSCP` by age and gender, percentage changes from NRS Local Authority Population Projections up to 2025 were calculated and applied to the 2022 mid-year population estimates. Note that NRS does produce HSCP-level population projections, which are used in HSCP profiles; the method described here only applies to locality-level projections.

2.  Care Home data included in the Services Map and Table was sourced from the [Care Inspectorate](https://www.careinspectorate.com/index.php/about-us). [GP Practice](https://www.opendata.nhs.scot/dataset/gp-practice-contact-details-and-list-sizes), [Hospital](https://www.opendata.nhs.scot/dataset/hospital-codes) and [A&E](https://www.opendata.nhs.scot/dataset/nhs-scotland-accident-emergency-sites) data were sourced from Public Health Scotland Open Data platform. Only services within the physical boundary of the HSCP or Locality are included in the map and table, so there may be services outside `r HSCP` that residents use but are not shown. Information on access deprivation was taken from the [ScotPHO profiles](https://scotland.shinyapps.io/ScotPHO_profiles_tool/) (The Scottish Public Health Observatory).

3.  Sourced from [ScotPHO](https://scotland.shinyapps.io/ScotPHO_profiles_tool/). More recent data may be available for the indicators elsewhere.

4.  ScotPHO data is often reported using the European Age-Sex Standardised Rate per 100,000. This allows for comparisons across different areas to be made. For more information on how these rates are calculated, please refer to the [PHS website: Geography, population and deprivation support](https://publichealthscotland.scot/services/geography-population-and-deprivation-support/population/){.uri}.

5.  Data on physical long-term conditions (LTC) is sourced from the Source Linkage Files (SLFs). These conditions are identified using ICD-9 and ICD-10 codes found in inpatient admissions' diagnosis fields for acute and mental health cases. Note that this data does not include all service users in Scotland diagnosed with an LTC, as not all of these individuals have utilized these services. Additionally, LTC rates are based on an adjusted population indicator in the Source Linkage Files, ensuring that the population sizes align more closely with official estimates.

##### Page Break

## Appendices

### Appendix 1: Indicator Definitions

```{r echo = FALSE, fig.width = 4, fig.height = 10, ft.split = TRUE}
knitr::kable(indicator_defs, format = "markdown")
```

##### Page break

### Appendix 2: Date of Indicator Data Extractions

```{r echo = FALSE, fig.width = 4, fig.height = 10, ft.split = TRUE}
knitr::kable(dates_extract, col.names = c("**Section**", "**Indicator**", "**Date of data extraction**"), format = "markdown")
```

##### Page Break

### Appendix 3: Conditions included as Potentially Preventable Admissions (PPAs)

```{r echo = FALSE, fig.width = 7, fig.height = 10, warning = FALSE}
knitr::kable(ppa_def, format = "markdown")
```
