---
title: ''
output:
  word_document:
    reference_docx: //conf/LIST_analytics/West Hub/02 - Scaled Up Work/RMarkdown/Locality
      Profiles/Master RMarkdown Document & Render Code/Locality_Profiles_Report_Template.docx
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(kableExtra.auto_format = FALSE)

#Line below for testing only
#LOCALITY <-  "Skye, Lochalsh and West Ross"
#LOCALITY <- "Falkirk West"
#LOCALITY <- "Stirling City with the Eastern Villages Bridge of Allan and Dunblane"
#LOCALITY <- "Ayr North and Former Coalfield Communities"
#LOCALITY <- "Helensburgh and Lomond"
#LOCALITY <- "City of Dunfermline"
HSCP <- "Moray"
print(getwd())
source("hscp_level/Demographics/1. Demographics - Population.R")
source("hscp_level/Demographics/2. Demographics - SIMD.R")

#test

x <- 1 #object for figure numbers
y <- 1 #object for table numbers

```

#####Page break

## Demographics

### Summary:

\newline

**For the most recent time periods available, `r LOCALITY` Locality had:**

+ A total population of **`r total_population`** people, where **`r gender_breakdown[gender_breakdown$sex == "M",]$perc`** were male, and **`r over65`%** were aged over 65.
+ **`r perc_top_quintile`%** of people lived in the least deprived SIMD quintile, and **`r perc_bottom_quintile`%** lived in the most deprived quintile.


### Population
<!-- Total Population Text -->
In `r pop_max_year`, the total population of `r LOCALITY` locality was `r total_population`. The graph below shows the population distribution of the locality. Overall, **`r gender_breakdown[gender_breakdown$sex == "M",]$perc`** of the population are male, and **`r gender_breakdown[gender_breakdown$sex == "F",]$perc`** are female.

####Figure `r x`: Population by age and sex.

\newline

```{r echo = FALSE, fig.width=6, fig.height= 3, warning = F}

pop_pyramid

x <- x +1
```

<!-- Population over time -->

Figure `r x` shows the historical population of `r LOCALITY`, along with the NRS population projections. `r pop_graph_text` `r pop_proj_text`. *Please see the footnotes for more information on how the population projections were calculated^1^.* 


#####Page break

####Figure `r x`: Population time trend and projection.
\newline

```{r echo = FALSE, fig.width= 7, fig.height= 3, warning = F}
pop_ts_plot

x <- x +1
```

\newline

Figure `r x` shows how population structure has changed between `r pop_min_year` and `r pop_max_year`.

####Figure `r x`: Change in population structure over the last five years.
\newline

```{r echo = FALSE, fig.width= 7, fig.height= 3.5, warning = F}
hist_pop_change

x <- x +1
```

##### Page break

### Deprivation
The following section explores the deprivation structure of `r LOCALITY` through the Scottish Index of Multiple Deprivation (SIMD). The SIMD ranks all datazones in Scotland by a number of factors; Access, Crime, Education, Employment, Health, Housing and Income. Based on these ranks, each datazone is then given an overall deprivation rank, which is used to split datazones into Deprivation Quintiles (Quintile 1 being the most deprived, and Quintile 5 the least). The most recent SIMD ranking was carried out in 2020. This section mainly focuses on the SIMD 2020 classifications, however the 2016 classifications are used to assess how deprivation has changed in `r LOCALITY` when compared to the rest of Scotland.

Of the `r pop_max_year` population in `r LOCALITY`, **`r perc_bottom_quintile`%** live in the most deprived Quintile (SIMD 1), and **`r perc_top_quintile`%** live in the least deprived Quintile (SIMD 5). 


####Figure `r x`: Map of Data Zones within `r LOCALITY` coloured by SIMD  quintiles.

```{r echo = FALSE, fig.width= 7, warning = F}
simd_map

x <- x + 1
```

##### Page break

The following table details the percentage of the 2016 population living in the 2016 SIMD Quintiles, the percentage of the `r pop_max_year` population living in the 2020 SIMD Quintiles, and their difference for comparison. Figure `r x` then breaks down SIMD by domain in `r LOCALITY`.

####Table `r y`: Percentage population living in the 2016 and 2020 SIMD Datazone Quintiles in 2016 and `r pop_max_year` respectively.
\newline

```{r echo = FALSE}
knitr::kable(simd_diff_overall, 
             col.names = c("**Quintile**", "**Percent of 2016 Population (SIMD 2016 Ranking)**",
                           "**Percent of 2021 Population (SIMD 2020 Ranking)**", "**Difference**"),
             align = c('l','r','r','r'))

y <- y + 1
```

\newline

####Figure `r x`: Proportion of the population that reside in each 2020 SIMD quintile by domain in `r pop_max_year`.
\newline

```{r echo = FALSE, fig.width= 7, fig.height=4, warning = F}
simd_domains

x <- x + 1
```


##### Page Break

Figure `r x` presents a comparison between the 2016 SIMD ranking applied to 2016 population estimates, and the more recent 2020 SIMD ranking applied to `r pop_max_year` population estimates. The percentages of the population living within each SIMD quintile by domain were calculated using the 2016 and 2020 SIMD datazone classifications respectively. The differences in these percentages are plotted in Figure 6. Negative values on the y-axis indicate a decrease in percent of the population living within a quintile, while positive values indicate an increase in percent of the population living within a quintile. **Please note that quintiles have been weighted by the Scottish population so, any local changes in SIMD quintile do not necessarily indicate a difference in deprivation, but rather a difference in deprivation in comparison to the rest of Scotland.**

\newline

####Figure `r x`: Percentage population in 2016 and `r pop_max_year` living in the 2016 and the 2020 SIMD quintiles by domain.

\newline

```{r echo = FALSE, fig.width= 7.5, fig.height= 7, warning = F}
simd_diff_plot

x <- x+1
```
